### 2017-08-12 01_actor_careers/article.Rmd
actor data

---
title: "How Old Actors?"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning=FALSE, message=FALSE)
```

## Intro

Stuff and text.

## Data

### Films

```{r}
library(readr)
library(dplyr)

films = read_csv("https://raw.githubusercontent.com/TMBish/lab_posts/master/01_actor_careers/full_film_data.csv")

films %>% glimpse()

```

### Actors / Directors

```{r}

library(gender)
library(stringr)

film_folk = read_csv("")

# Grep out first name and dob year for the gender function
film_folk = 
  film_folk %>%
  mutate(
    first_name = str_extract(name, "(?i)[a-z]+(?=\\s)"),
    dob_year = 1940
  )

# Distinct name, dob combos and predict gender
genders = 
  film_folk %>% 
  distinct(first_name, dob_year) %>%
  gender_df(name_col = "first_name", year_col = "dob_year") %>%
  select(name, gender, "dob_year" = year_min)

# Join back the gender back to the main data
film_folk = 
  film_folk %>%
  inner_join(genders)

```

We should sense check the gender mapping. Let's take a random 10 people to check:

```{r}

```

## Measuring Performance

To investigate our hypothesis we need to make a couple of assumptions. Since we don't have an individual actor / director box score (like we would in sporting match) we'll have to assume an actor / director has a tangible affect on the quality of the movie; a relatively safe assumption.

Further, for actors we'll have to limit the data to actors that played an important enough role in the film to affect the overall quality of the film. So while Michael Cera's cameo in *This is the End* was high quality he can't be said to influence the rotten tomatoes rating of the film on his own.

<iframe width="560" height="315" src="https://www.youtube.com/watch?v=qIKPJlKHKxg" frameborder="0" allowfullscreen></iframe>

### 2017-08-12 01_actor_careers/analysis.R

@@ -1,0 +1,11 @@
+library(readr)
+library(dplyr)
+library(highcharter)
+library(ggplot2)
+
+
+
+films = read_csv("https://raw.githubusercontent.com/TMBish/lab_posts/master/01_actor_careers/full_film_data.csv")
+
+
+

### 2017-08-12 01_actor_careers/get_bio.R

@@ -1,4 +1,4 @@
-get_actor_details = function(actor) {
+get_bio = function(person) {
   
   require(rvest)
   require(stringr)
@@ -7,8 +7,8 @@ get_actor_details = function(actor) {
   require(lubridate)
   
   # Format URL
-  actor_string = str_replace_all(str_replace_all(tolower(actor), " ", "_"),"[\\-\\.]"," ")
-  celeb_url = sprintf("https://www.rottentomatoes.com/celebrity/%s/", actor_string)
+  person_string = str_replace_all(str_replace_all(tolower(person), " ", "_"),"[\\-\\.]"," ")
+  celeb_url = sprintf("https://www.rottentomatoes.com/celebrity/%s/", person_string)
 
   output_object = tryCatch({
       

### 2017-08-12 01_actor_careers/master.R

@@ -29,12 +29,12 @@ library(parallel)
 
 options(stringsAsFactors = FALSE)
 
-actors = 
-  read_csv("https://raw.githubusercontent.com/TMBish/Stratton/master/data/actors.csv") %>%
-  mutate(dob = ymd(19900101))
+actors = read_csv("https://raw.githubusercontent.com/TMBish/Stratton/master/data/actors.csv")
 
-directors = 
-  read_csv("https://raw.githubusercontent.com/TMBish/Stratton/master/data/directors.csv") %>%
+directors = read_csv("https://raw.githubusercontent.com/TMBish/Stratton/master/data/directors.csv")
+
+film_folk = actors %>%
+  union_all(directors) %>%
   mutate(dob = ymd(19900101))
 
 films = data.frame(
@@ -57,54 +57,53 @@ films = data.frame(
 
 start_time = Sys.time()
 
-# 1:nrow(actors
-
-for (row in 1:nrow(directors)) {
+for (row in 1:nrow(film_folk)) {
   
-  actor = directors$Name[row]
+  person = film_folk$Name[row]
   
   # Call the get_actor_details function
-  details = get_actor_details(actor)
+  details = get_bio(person)
+  
   if (length(details$url)== 1 && is.na(details$urls) || nrow(details$urls) == 0) { next }
   
   # Log the actor details to the console
-  cat(glue("Actor: {actor} || DOB: {details$dob} || Number of URLS: {nrow(details$urls)}"),"\n") 
+  cat(glue("Actor: {person} || DOB: {details$dob} || Number of URLS: {nrow(details$urls)}"),"\n") 
   
   # Add DOB to actor / director table
-  actors[row,"dob"] = details$dob
+  film_folk[row,"dob"] = details$dob
 
   # Get URLS
-  urls = details$url %>% distinct(url_extension)
+  # urls = details$url %>% distinct(url_extension)
   
-  # DRY = DON'T REPEAT YOURSELF
-  if ( nrow(films) > 0) {
-    # Remove movies we've already scraped
-    starting_rows = nrow(urls)
-    urls = 
-      urls %>%
-      anti_join(films %>% select(url), by = c("url_extension" = "url"))
+  # # DRY = DON'T REPEAT YOURSELF
+  # if ( nrow(films) > 0) {
+  #   # Remove movies we've already scraped
+  #   starting_rows = nrow(urls)
+  #   urls = 
+  #     urls %>%
[…]

### 2017-08-13 01_actor_careers/05_report.Rmd
Update

---
title: "How Old Actors?"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning=FALSE, message=FALSE)
```

## Intro

Stuff and text.

## Data

### Films

```{r}
library(readr)
library(dplyr)

films = read_csv("https://raw.githubusercontent.com/TMBish/lab_posts/master/01_actor_careers/full_film_data.csv") %>%
  filter(!is.na(title))

films %>% glimpse()

```

### Actors / Directors

```{r}

library(gender)
library(stringr)
library(lubridate)

film_folk = read_csv("https://raw.githubusercontent.com/TMBish/lab_posts/master/01_actor_careers/actors_directors.csv")

film_folk[film_folk$dob < as.Date("1880-01-01"), "dob"] = as.Date("1880-01-01")

# Grep out first name and dob year for the gender function
film_folk = 
  film_folk %>%
  mutate(
    first_name = str_extract(name, "(?i)[a-z]+(?=\\s)"),
    dob_year = year(dob)
  )

# Distinct name, dob combos and predict gender
genders = 
  film_folk %>% 
  distinct(first_name, dob_year) %>%
  gender_df(name_col = "first_name", year_col = "dob_year") %>%
  select("first_name" = name, gender, "dob_year" = year_min)

```

We should sense check the gender mapping. Let's take a random 10 people to check:

```{r}
genders %>%
  sample_n(10) %>%
  knitr::kable(caption = "Sense Checking the Gender Mapping")

```

Looks pretty, pretty, pretty good.

```{r}
# Join back the gender back to the main data
film_folk = 
  film_folk %>%
  left_join(genders)

```

## Measuring Performance

To investigate our hypothesis we need to make a couple of assumptions. Since we don't have an individual actor / director box score (like we would in sporting match) we'll have to assume an actor / director has a tangible affect on the quality of the movie; a relatively safe assumption.

Further - for actors - we'll have to limit the dataset to actors that played an important role in the film to the extent that they affected the overall quality of the film. So while Michael Cera's cameo in *This is the End* was high quality it can't be said that he influenced the rotten tomatoes rating of the film on his own.

<iframe width="560" height="315" src="https://www.youtube.com/v/qIKPJlKHKxg" frameborder="0" allowfullscreen></iframe>

### 2017-08-13 01_actor_careers/04_analyse.R

@@ -1,0 +1,190 @@
+library(readr)
+library(dplyr)
+library(highcharter)
+library(ggplot2)
+library(tidyr)
+library(gender)
+library(stringr)
+library(lubridate)
+
+# Data --------------------------------------------------------------------
+films = read_csv("https://raw.githubusercontent.com/TMBish/lab_posts/master/01_actor_careers/full_film_data.csv") %>%
+  filter(!is.na(title))
+
+
+film_folk = read_csv("https://raw.githubusercontent.com/TMBish/lab_posts/master/01_actor_careers/actors_directors.csv")
+film_folk[film_folk$dob < as.Date("1880-01-01"), "dob"] = as.Date("1880-01-01")
+
+# Grep out first name and dob year for the gender function
+film_folk = 
+  film_folk %>%
+  mutate(
+    first_name = str_extract(name, "(?i)[a-z]+(?=\\s)"),
+    dob_year = year(dob)
+  )
+  
+# Distinct name, dob combos and predict gender
+genders = 
+  film_folk %>% 
+  distinct(first_name, dob_year) %>%
+  gender_df(name_col = "first_name", year_col = "dob_year") %>%
+  select("first_name" = name, gender, "dob_year" = year_min)
+
+film_folk = 
+  film_folk %>%
+  left_join(genders)
+
+ # The deal with directors? --------------------------------------------------------------------
+dir_data =
+  films %>% 
+  select("name" = director) %>%
+  inner_join(film_folk) %>%
+  group_by(gender) %>%
+  summarise(
+  	films = n()
+  ) %>%
+  filter(!is.na(gender))
+
+# Most are men Yep
+
+ # Volumes By Age --------------------------------------------------------------------
+
+volume_data =
+  films %>% 
+  select(title, year, tomatometer, director, actor_1:actor_3) %>%
+  gather("role", "name", director, actor_1:actor_3) %>%
+  mutate(role = ifelse(role == "director", "Director", "Actor")) %>%
+  inner_join(film_folk) %>%
+  mutate(
+    age_at_production = year - dob_year
+  ) %>%
+  filter(between(age_at_production, 10,100)) %>%
+  select(name, gender, dob_year, age_at_production, year, role, tomatometer)
+
+
+	# Ggplot
+	var = "Director"
+	temp = 
+		volume_data %>%
+		filter(
+			role == var,
[…]

### 2017-08-13 01_actor_careers/analysis.R

@@ -1,11 +1,0 @@
-library(readr)
-library(dplyr)
-library(highcharter)
-library(ggplot2)
-
-
-
-films = read_csv("https://raw.githubusercontent.com/TMBish/lab_posts/master/01_actor_careers/full_film_data.csv")
-
-
-

### 2017-08-13 01_actor_careers/render_article.R

@@ -1,0 +1,4 @@
+library(knitr)
+
+
+rmarkdown::render("C:/Users/Tom Bishop/Desktop/lab_posts/01_actor_careers/article.Rmd", output_file = "output.html")

### 2017-08-13 01_actor_careers/scraps.R

@@ -1,0 +1,78 @@
+
+library(tidyr)
+
+data =
+  films %>% 
+  select(title, year, tomatometer, director, actor_1:actor_3) %>%
+  gather("role", "name", director, actor_1:actor_3) %>%
+  mutate(role = ifelse(role == "director", "Director", "Actor")) %>%
+  inner_join(film_folk) %>%
+  mutate(
+    age_at_production = year - dob_year
+  ) %>%
+  filter(between(age_at_production, 10,100)) 
+
+write_csv(data, "C:/Users/Tom Bishop/Desktop/test.csv")
+
+
+chart_data = 
+  data %>%
+  mutate(age_at_production = as.character(age_at_production)) %>%
+  group_by(age_at_production) %>%
+  summarise(films = n())
+
+test = hchart(chart_data, "column", hcaes(x = age_at_production, y = films)) %>%
+  hc_add_theme(tmbish)
+
+
+chart_data = 
+  data %>%
+  mutate(age_at_production = as.character(age_at_production)) %>%
+  group_by(age_at_production, role) %>%
+  summarise(films = n()) %>%
+  spread(role, films)
+
+test = hchart(chart_data, "column", hcaes(x = age_at_production, y = films, group = role)) %>%
+  hc_add_theme(tmbish)
+
+actor = density(chart_data$Actor[!is.na(chart_data$Actor)])
+director = density(chart_data$Director[!is.na(chart_data$Director)])
+
+highchart() %>% 
+  hcdensity(actor) %>%
+  hc_add
+
+
+
+test = 
+  films %>%
+  inner_join(film_folk, by = c("director" =  "name")) %>%
+  mutate(
+    age_at_production = year - dob_year
+  ) %>%
+  filter(age_at_production > 20) %>%
+  mutate(age_bucket = )
+
+chart_data = 
+  test %>%
+  mutate(age_bucket = paste(round(age_at_production/10) *10, "-", round(age_at_production/10) *10 + 10)) %>%
+  select(tomatometer, age_bucket)
+  
+
+library(highcharter)
+test_chart = 
+  hchart(chart_data, "scatter", hcaes(x = age_at_production, y = tomatometer)) %>%
+  hc_theme(tmbish)
+
+test_chart = 
+  hcboxplot(x = chart_data$tomatometer, var = chart_data$age_bucket) %>%
+  hc_add_theme(tmbish)
+
+highchart() %>%
[…]

### 2017-08-15 01_actor_careers/05_report.Rmd
Working on JS interactivity

@@
 title: "How Old Actors?"
-output: html_document
+output: 
+  html_document:
+    code_folding: hide
 ---
@@
 library(dplyr)
+library(tidyr)
 
-films = read_csv("https://raw.githubusercontent.com/TMBish/lab_posts/master/01_actor_careers/full_film_data.csv") %>%
+films = read_csv("https://raw.githubusercontent.com/TMBish/lab_posts/master/01_actor_careers/00_full_film_data.csv") %>%
   filter(!is.na(title))
-
-films %>% glimpse()
 
@@
 
-film_folk = read_csv("https://raw.githubusercontent.com/TMBish/lab_posts/master/01_actor_careers/actors_directors.csv")
+film_folk = read_csv("https://raw.githubusercontent.com/TMBish/lab_posts/master/01_actor_careers/00_actors_directors.csv")
 
@@
 
+## Gender Gap
+
+Some text.
+Some text.
+Some text.
+Some text.Some text.
+Some text.
+Some text.
+Some text.
+Some text.
+Some text.
+Some text.
+
+```{r}
+library(highcharter)
+tmbish = 
+  hc_theme(
+    chart = list(
+      backgroundColor = list("white"),
+      style = list(
+        fontFamily = "Droid Sans"
+      )
+    ),
+    colors = list("#414141", "#FF6A5C", "#CCDFC8", "#056571"),
+    title = list(
+      style = list(fontWeight = "bold", color = "#414141"),
+      align = "left"
+    ),
+    xAxis = list(
+      gridLineColor = "#2196F3",
+      lineColor = "#2196F3",
+      gridLineWidth = 0.5,
+      lineWidth = 0,
+      title = list(style = list(fontWeight = "bold"))
+    ),
+    yAxis = list(
+      gridLineColor = "#2196F3",
+      lineColor = "#2196F3",
+      gridLineWidth = 0.5,
+      lineWidth = 0,
+      title = list(style = list(weight = "bold"))
+    ),
+    subtitle = list(
+      style = list(fontStyle = "italic", color ="#414141"), 
+      align = "left"
+    ),
+    tooltip = list(
+      borderWidth = 0,
+      shape = "square",
+      valueDecimals = 2
+    )
+  )
+
+volume_data =
+  films %>% 
+  select(title, year, tomatometer, director, actor_1:actor_3) %>%
+  gather("role", "name", director, actor_1:actor_3) %>%
+  mutate(role = ifelse(role == "director", "Director", "Actor")) %>%
+  inner_join(film_folk) %>%
+  mutate(
+    age_at_production = year - dob_year
+  ) %>%
+  filter(between(age_at_production, 10,100)) %>%
+  select(name, gender, dob_year, age_at_production, year, role, tomatometer)
+
+  temp = 
+    volume_data %>%
+    filter(
+      !is.na(gender)
+    ) %>%
+    mutate(
+      category = case_when(
+        role == "Director" ~ "director",
+        gender == "male" ~ "male_actor",
+        TRUE ~ "female_actor"
+      )
+    ) %>% 
+    group_by(category, age_at_production) %>%
+    summarise(films = n()) %>%
+    group_by(category) %>%
+    mutate(percentage = films / sum(films))
+
+```
+
+<div id = "tester">
+```{r}
+chart_data = 
+temp %>%
+select(-films) %>%
+spread(category, percentage) %>%
+mutate(
+  director_cdf = cumsum(ifelse(!is.na(director), director, 0)),
+  female_actor_cdf = cumsum(ifelse(!is.na(female_actor), female_actor, 0)),
+  male_actor_cdf = cumsum(ifelse(!is.na(male_actor), male_actor, 0))
+)
+
+female_cdf = chart_data$female_actor_cdf
+female_pdf = chart_data$female_actor
+male_cdf = chart_data$male_actor_cdf
+male_pdf = chart_data$male_actor
+dir_cdf = chart_data$director_cdf %>% round(2)
+dir_pdf = chart_data$director
+
+chart = 
+  highchart() %>%
+  hc_add_theme(tmbish) %>%
+  hc_xAxis(
+    categories = chart_data$age_at_production,
+    title = list(text = "Age at Production")
+  ) %>%
+  hc_yAxis(
+    labels = list(formatter = JS("function(){return(Math.round(this.value * 1000) / 10 + '%')}"))
+  ) %>%
+  hc_title(text = "Female actors") %>%
+  hc_subtitle(text = "Comparing male actors, (male) directors and female actors") %>%
+  hc_add_series(name = "Director", type = "spline", data = chart_data$director) %>%
+  hc_add_series(name = "Male Actor", type = "spline", data = chart_data$male_actor) %>%
+  hc_add_series(
+    name = "Female Actor",
+    type = "area",
+    data = chart_data$female_actor,
+    zIndex = -10,
+    marker = list(enabled = FALSE),
+    fillOpacity = 0.5
+  )
+
+chart
+```
+</div>
+
+<button id = "button">Button</button>
+
 ## Measuring Performance
@@
 <iframe width="560" height="315" src="https://www.youtube.com/v/qIKPJlKHKxg" frameborder="0" allowfullscreen></iframe>
+
+## Housekeeping
+
+<script>
+
+$(document).ready(function() {
+    $("#button").click(function(){
+
+        var chart=$("#tester").find(".highchart").highcharts();
+
+        if (chart.yAxis[0].getExtremes().dataMax == 1) {
+
+        } else {
+
+          chart.yAxis[0].setExtremes(0,`1`);
+          data = `dir_cdf`;
+          alert(data);
+          <!--chart.series[0].setData(`JS(paste0("[", dir_cdf %>% paste(collapse = ","), "]"))`); -->
+        };
+
+    }); 
+});
+
+</script>

### 2017-08-15 01_actor_careers/04_analyse.R

@@ -177,8 +177,6 @@ volume_data =
 	    fillOpacity = 0.5
 	  )
 
-
-
  # Volumes By Age --------------------------------------------------------------------
 
 

### 2017-08-16 01_actor_careers/05_report.Rmd
JS pass

@@
 ---
-title: "How Old Actors?"
+title: "Test RMD"
 output: 
@@
 
-female_cdf = chart_data$female_actor_cdf
-female_pdf = chart_data$female_actor
-male_cdf = chart_data$male_actor_cdf
-male_pdf = chart_data$male_actor
-dir_cdf = chart_data$director_cdf %>% round(2)
-dir_pdf = chart_data$director
+convert_js_vec = function(vec) {
+
+  js_string = vec %>% round(2) %>% paste(collapse = ",")
+
+  return(JS( paste0("[", js_string, "]") ))
+
+}
+
+female_cdf = chart_data$female_actor_cdf %>% convert_js_vec()
+female_pdf = chart_data$female_actor %>% convert_js_vec()
+male_cdf = chart_data$male_actor_cdf %>% convert_js_vec()
+male_pdf = chart_data$male_actor %>% convert_js_vec()
+dir_cdf = chart_data$director_cdf %>% convert_js_vec()
+dir_pdf = chart_data$director %>% convert_js_vec()
 
@@
 
-          chart.yAxis[0].setExtremes(0,`1`);
-          data = `dir_cdf`;
-          alert(data);
-          <!--chart.series[0].setData(`JS(paste0("[", dir_cdf %>% paste(collapse = ","), "]"))`); -->
+          chart.yAxis[0].setExtremes(0,`r 1`);
+          var dat = `r JS(paste0("[", dir_cdf %>% paste(collapse=",") , "]") )`;
+          alert(dat);
+          chart.series[0].setData(dat);
         };

### 2017-08-16 01_actor_careers/05_report.Rmd
JS data viz complete

--- 2017-08-13 01_actor_careers/05_report.Rmd
@@
 ---
-title: "How Old Actors?"
-output: html_document
+title: "Test RMD"
+output: 
+  html_document:
+    code_folding: hide
 ---
@@
 
-library(gender)
-library(stringr)
-library(lubridate)
-
-film_folk = read_csv("https://raw.githubusercontent.com/TMBish/lab_posts/master/01_actor_careers/actors_directors.csv")
-
-film_folk[film_folk$dob < as.Date("1880-01-01"), "dob"] = as.Date("1880-01-01")
-
-# Grep out first name and dob year for the gender function
-film_folk = 
-  film_folk %>%
-  mutate(
-    first_name = str_extract(name, "(?i)[a-z]+(?=\\s)"),
-    dob_year = year(dob)
-  )
-
-# Distinct name, dob combos and predict gender
-genders = 
-  film_folk %>% 
-  distinct(first_name, dob_year) %>%
-  gender_df(name_col = "first_name", year_col = "dob_year") %>%
-  select("first_name" = name, gender, "dob_year" = year_min)
+# library(gender)
+# library(stringr)
+# library(lubridate)
+# 
+# film_folk = read_csv("https://raw.githubusercontent.com/TMBish/lab_posts/master/01_actor_careers/00_actors_directors.csv")
+# 
+# film_folk[film_folk$dob < as.Date("1880-01-01"), "dob"] = as.Date("1880-01-01")
+# 
+# # Grep out first name and dob year for the gender function
+# film_folk = 
+#   film_folk %>%
+#   mutate(
+#     first_name = str_extract(name, "(?i)[a-z]+(?=\\s)"),
+#     dob_year = year(dob)
+#   )
+#   
+# # Distinct name, dob combos and predict gender
+# genders = 
+#   film_folk %>% 
+#   distinct(first_name, dob_year) %>%
+#   gender_df(name_col = "first_name", year_col = "dob_year") %>%
+#   select("first_name" = name, gender, "dob_year" = year_min)
 
@@
 
+## Gender Gap
+
+Some text.
+Some text.
+Some text.
+Some text.Some text.
+Some text.
+Some text.
+Some text.
+Some text.
+Some text.
+Some text.
+
+```{r}
+library(highcharter)
+tmbish = 
+  hc_theme(
+    chart = list(
+      backgroundColor = list("white"),
+      style = list(
+        fontFamily = "Droid Sans"
+      )
+    ),
+    colors = list("#414141", "#FF6A5C", "#CCDFC8", "#056571"),
+    title = list(
+      style = list(fontWeight = "bold", color = "#414141"),
+      align = "left"
+    ),
+    xAxis = list(
+      gridLineColor = "#2196F3",
+      lineColor = "#2196F3",
+      gridLineWidth = 0.5,
+      lineWidth = 0,
+      title = list(style = list(fontWeight = "bold"))
+    ),
+    yAxis = list(
+      gridLineColor = "#2196F3",
+      lineColor = "#2196F3",
+      gridLineWidth = 0.5,
+      lineWidth = 0,
+      title = list(style = list(weight = "bold"))
+    ),
+    subtitle = list(
+      style = list(fontStyle = "italic", color ="#414141"), 
+      align = "left"
+    ),
+    tooltip = list(
+      borderWidth = 0,
+      shape = "square",
+      valueDecimals = 2
+    )
+  )
+
+volume_data =
+  films %>% 
+  select(title, year, tomatometer, director, actor_1:actor_6) %>%
+  gather("role", "name", director, actor_1:actor_6) %>%
+  mutate(role = ifelse(role == "director", "Director", "Actor")) %>%
+  inner_join(film_folk) %>%
+  mutate(
+    age_at_production = year - dob_year
+  ) %>%
+  filter(between(age_at_production, 10,100)) %>%
+  select(name, gender, dob_year, age_at_production, year, role, tomatometer)
+
+  temp = 
+    volume_data %>%
+    filter(
+      !is.na(gender)
+    ) %>%
+    mutate(
+      category = case_when(
+        role == "Director" ~ "director",
+        gender == "male" ~ "male_actor",
+        TRUE ~ "female_actor"
+      )
+    ) %>% 
+    group_by(category, age_at_production) %>%
+    summarise(films = n()) %>%
+    group_by(category) %>%
+    mutate(percentage = films / sum(films))
+
+```
+
+<div id = "age_series_chart">
+```{r}
+chart_data = 
+temp %>%
+select(-films) %>%
+spread(category, percentage) %>%
+mutate(
+  director = ifelse(!is.na(director), director, 0),
+  female_actor = ifelse(!is.na(female_actor), female_actor, 0),
+  male_actor = ifelse(!is.na(male_actor), male_actor, 0),
+  director_cdf = cumsum(director),
+  female_actor_cdf = cumsum(female_actor),
+  male_actor_cdf = cumsum(male_actor)
+)
+
+convert_js_vec = function(vec) {
+
+  js_string = vec %>% round(4) %>% paste(collapse = ",")
+
+  return(JS( paste0("[", js_string, "]") ))
+
+}
+
+# For the javascript client side interactivity on the age series chart
+female_cdf = chart_data$female_actor_cdf %>% convert_js_vec()
+female_pdf = chart_data$female_actor %>% convert_js_vec()
+male_cdf = chart_data$male_actor_cdf %>% convert_js_vec()
+male_pdf = chart_data$male_actor %>% convert_js_vec()
+dir_cdf = chart_data$director_cdf %>% convert_js_vec()
+dir_pdf = chart_data$director %>% convert_js_vec()
+
+chart = 
+  highchart() %>%
+  hc_add_theme(tmbish) %>%
+  hc_chart(
+    animation = list(duration = 2000)
+  ) %>%
+  hc_xAxis(
+    categories = chart_data$age_at_production,
+    title = list(text = "Age at Production")
+  ) %>%
+  hc_yAxis(
+    title = list(text = "Probablity Density"),
+    labels = list(formatter = JS("function(){return(Math.round(this.value * 1000) / 10 + '%')}"))
+  ) %>%
+  hc_title(text = "Female actors") %>%
+  hc_subtitle(text = "Comparing male actors, (male) directors and female actors") %>%
+  hc_add_series(
+    name = "Director", 
+    type = "spline",
+    data = chart_data$director,
+    marker = list(enabled = FALSE)
+  ) %>%
+  hc_add_series(
+    name = "Male Actor",
+    type = "spline",
+    data = chart_data$male_actor,
+    marker = list(enabled = FALSE)
+  ) %>%
+  hc_add_series(
+    name = "Female Actor",
+    type = "area",
+    data = chart_data$female_actor,
+    zIndex = -10,
+    marker = list(enabled = FALSE),
+    fillOpacity = 0.5
+  )
+
+chart
+```
+</div>
+
+<button id = "update_age_series"> Show Cumulative Distribution </button>
+
 ## Measuring Performance
 
-To investigate our hypothesis we need to make a couple of assumptions.
-Since we don't have an individual actor / director box score (like we would in sporting match) we'll have to assume an actor / director has a tangible affect on the quality of the movie; a relatively safe assumption.
+To investigate our hypothesis we must make a couple of assumptions.
+Since we don't have an individual actor / director performance (like we would have for players in a sporting contest for example) we'll have to assume an actor or director can have a tangible affect on the quality of the movie they appear in; there are obviously many other factors but this seems like a relatively safe assumption.
 
-Further - for actors - we'll have to limit the dataset to actors that played an important role in the film to the extent that they affected the overall quality of the film.
-So while Michael Cera's cameo in *This is the End* was high quality it can't be said that he influenced the rotten tomatoes rating of the film on his own.
+Further - for actors - we'll have to limit the dataset to actors that played an important role in the film.
+They  need to be prominent enough so as to affect the overall quality of the film.
+So while Michael Cera's cameo in *This is the End* was quality it can't be said that he influenced the rotten tomatoes rating of the film on his own.
 
-<iframe width="560" height="315" src="https://www.youtube.com/v/qIKPJlKHKxg" frameborder="0" allowfullscreen></iframe>
+<iframe width="560" height="315" src="https://www.youtube.com/embed/qIKPJlKHKxg" frameborder="0" allowfullscreen></iframe>
+
+After looking through a few rotten tomatoes pages it seems limiting to the top 3 actors in a given film is a good rule of thumb for at least partially influncial performances.
+
+### Average Performance by Age
+
+## Housekeeping
+
+<script>
+
+  $(document).ready(function() {
+
+  var show_cdf = false;
+
+    $("#update_age_series").click(function(){
+
+        var chart=$("#age_series_chart").find(".highchart").highcharts();
+
+        if (show_cdf) {
+
+          chart.yAxis[0].setExtremes(0,null);
+          chart.yAxis[0].setTitle({text:"Probability Density", redraw:false});
+          dir_pdf = `r dir_pdf`;
+          female_pdf = `r female_pdf`;
+          male_pdf = `r male_pdf`;
+          chart.series[0].setData(dir_pdf);
+          chart.series[1].setData(male_pdf);
+          chart.series[2].setData(female_pdf);
+          $("#update_age_series").html("Show Cumulative Distribution");
+
+        } else {
+
+          chart.yAxis[0].setExtremes(0,1);
+          chart.yAxis[0].setTitle({text:"Cumulative Probability", redraw:false});
+          dir_cdf = `r dir_cdf`;
+          female_cdf = `r female_cdf`;
+          male_cdf = `r male_cdf`;
+          chart.series[0].setData(dir_cdf);
+          chart.series[1].setData(male_cdf);
+          chart.series[2].setData(female_cdf);
+
+          $("#update_age_series").html("Show Density");
+        };
+
+        show_cdf = !show_cdf
+
+    }); 
+  });
+
+</script>

### 2017-08-16 01_actor_careers/04_analyse.R

@@ -51,8 +51,8 @@ dir_data =
 
 volume_data =
   films %>% 
-  select(title, year, tomatometer, director, actor_1:actor_3) %>%
-  gather("role", "name", director, actor_1:actor_3) %>%
+  select(title, year, tomatometer, director, actor_1:actor_6) %>%
+  gather("role", "name", director, actor_1:actor_6) %>%
   mutate(role = ifelse(role == "director", "Director", "Actor")) %>%
   inner_join(film_folk) %>%
   mutate(
@@ -177,12 +177,72 @@ volume_data =
 	    fillOpacity = 0.5
 	  )
 
- # Volumes By Age --------------------------------------------------------------------
+ # Ratings By Age --------------------------------------------------------------------
 
-
+rating_data =
+  films %>% 
+  select(title, year, tomatometer, director, actor_1) %>%
+  gather("role", "name", director, actor_1) %>%
+  mutate(role = ifelse(role == "director", "Director", "Actor")) %>%
+  inner_join(film_folk) %>%
+  mutate(
+    age_at_production = year - dob_year
+  ) %>%
+  filter(between(age_at_production, 18,85)) %>%
+  select(name, gender, dob_year, age_at_production, year, role, tomatometer)
 
 
 temp = 
-	volume_data %>%
-	group_by(year) %>%
-	summarise(av_score = mean(tomatometer))
+	rating_data %>%
+	filter(
+		!is.na(gender)
+	) %>%
+	mutate(
+		category = case_when(
+			role == "Director" ~ "director",
+			gender == "male" ~ "male_actor",
+			TRUE ~ "female_actor"
+		)
+	) %>% 
+	group_by(category, age_at_production) %>%
+	summarise(rating = mean(tomatometer))
+
+chart_data = 
+	temp %>%
+	spread(category, rating)
+
+chart = 
+  highchart() %>%
+  hc_add_theme(tmbish) %>%
+  hc_chart(
+    animation = list(duration = 2000)
+  ) %>%
+  hc_xAxis(
+    categories = chart_data$age_at_production,
+    title = list(text = "Age at Production")
+  ) %>%
+  hc_yAxis(
+    title = list(text = "Probablity Density")
+  ) %>%
+  hc_title(text = "Female actors") %>%
+  hc_subtitle(text = "Comparing male actors, (male) directors and female actors") %>%
+  hc_add_series(
+    name = "Director", 
+    type = "spline",
[…]

### 2017-08-17 01_actor_careers/04_analyse.R
prog

@@ -8,11 +8,11 @@ library(stringr)
 library(lubridate)
 
 # Data --------------------------------------------------------------------
-films = read_csv("https://raw.githubusercontent.com/TMBish/lab_posts/master/01_actor_careers/full_film_data.csv") %>%
+films = read_csv("https://raw.githubusercontent.com/TMBish/lab_posts/master/01_actor_careers/00_full_film_data.csv") %>%
   filter(!is.na(title))
 
 
-film_folk = read_csv("https://raw.githubusercontent.com/TMBish/lab_posts/master/01_actor_careers/actors_directors.csv")
+film_folk = read_csv("https://raw.githubusercontent.com/TMBish/lab_posts/master/01_actor_careers/00_actors_directors.csv")
 film_folk[film_folk$dob < as.Date("1880-01-01"), "dob"] = as.Date("1880-01-01")
 
 # Grep out first name and dob year for the gender function
@@ -181,35 +181,32 @@ volume_data =
 
 rating_data =
   films %>% 
-  select(title, year, tomatometer, director, actor_1) %>%
-  gather("role", "name", director, actor_1) %>%
-  mutate(role = ifelse(role == "director", "Director", "Actor")) %>%
+  select(title, year, tomatometer, director, actor_1:actor_3) %>%
+  gather("role", "name", director, actor_1:actor_3) %>%
   inner_join(film_folk) %>%
+  filter(!is.na(gender)) %>%
   mutate(
-    age_at_production = year - dob_year
-  ) %>%
-  filter(between(age_at_production, 18,85)) %>%
-  select(name, gender, dob_year, age_at_production, year, role, tomatometer)
-
-
-temp = 
-	rating_data %>%
-	filter(
-		!is.na(gender)
-	) %>%
-	mutate(
-		category = case_when(
-			role == "Director" ~ "director",
+    age_at_production = year - dob_year,
+    category = case_when(
+			role == "director" ~ "director",
 			gender == "male" ~ "male_actor",
 			TRUE ~ "female_actor"
-		)
-	) %>% 
-	group_by(category, age_at_production) %>%
-	summarise(rating = mean(tomatometer))
-
-chart_data = 
-	temp %>%
-	spread(category, rating)
+	)
+  ) %>%
+  filter(between(age_at_production, 15,79)) %>%
+  select(name, gender, age_at_production, category, tomatometer) %>%
+  group_by(name) %>% 
+  mutate(
[…]

### 2017-08-18 01_actor_careers/04_analyse.R
tinker

@@ -193,20 +193,27 @@ rating_data =
 			TRUE ~ "female_actor"
 	)
   ) %>%
-  filter(between(age_at_production, 15,79)) %>%
+  filter(between(age_at_production, 15,85)) %>%
   select(name, gender, age_at_production, category, tomatometer) %>%
   group_by(name) %>% 
   mutate(
   	average_tomato  = mean(tomatometer),
   	films = n()
   ) %>% ungroup() %>%
-  filter(films >= 10) %>%
+  filter(films >= 5) %>%
   mutate(
-  	age_bucket =  paste(round(age_at_production/5) *5, "-", round(age_at_production/5) *5 + 5),
   	index = tomatometer / average_tomato) %>%
-  group_by(category, age_bucket) %>%
+  group_by(category, age_at_production) %>%
   summarise(rating = mean(index)) %>%
   spread(category, rating)
+
+# LOESS Trend Line
+loess_fit = loess(value ~ age_at_production , 
+                  data = rating_data %>% gather("role", "value", -age_at_production)
+                  # %>% group_by(age_at_production) %>% summarise(value = mean(value, na.rm = TRUE))
+                  )
+	
+predictions = loess_fit %>% predict(seq(15,85))
 
 chart = 
   highchart() %>%
@@ -215,29 +222,41 @@ chart =
     animation = list(duration = 2000)
   ) %>%
   hc_xAxis(
-    categories = rating_data$age_bucket,
+    categories = rating_data$age_at_production,
     title = list(text = "Age at Production")
   ) %>%
   hc_yAxis(
-    title = list(text = "Probablity Density")
+    title = list(text = "Probablity Density"),
+    min = 0.6
   ) %>%
   hc_title(text = "Female actors") %>%
   hc_subtitle(text = "Comparing male actors, (male) directors and female actors") %>%
   hc_add_series(
-    name = "Director", 
-    type = "line",
+    name = "Director",
+    type = "scatter",
     data = rating_data$director,
-    marker = list(enabled = FALSE)
-  ) %>%
+    marker = list(radius = 3, symbol = "circle")
+    ) %>%
   hc_add_series(
     name = "Male Actor",
-    type = "line",
+    type = "scatter",
     data = rating_data$male_actor,
-    marker = list(enabled = FALSE)
-  ) %>%
+    marker = list(radius = 3, symbol = "circle")
+    ) %>%
   hc_add_series(
     name = "Female Actor",
-    type = "line",
[…]

### 2017-08-18 01_actor_careers/render_article.R

@@ -1,4 +1,4 @@
 library(knitr)
 
 
-rmarkdown::render("C:/Users/Tom Bishop/Desktop/lab_posts/01_actor_careers/article.Rmd", output_file = "output.html")
+rmarkdown::render("C:/Users/Tom Bishop/Desktop/lab_posts/01_actor_careers/05_report.Rmd")

### 2017-08-22 01_actor_careers/05_report.Rmd
fixes and theme added

@@
 ---
-title: "Test RMD"
+title: "Films: Age & Gender"
 output: 
@@
 
-```{r setup, include=FALSE}
-knitr::opts_chunk$set(echo = TRUE, warning=FALSE, message=FALSE)
-```
+# Questions?
 
-## Intro
+Let's say we had a couple of questions about actors and directors:
 
-Stuff and text.
+> Do actors and directors improve with age?
 
-## Data
+> Are female actors generally cast  than their male counterparts?
 
-### Films
+To answer these questions we're going to need some data.
+
+# Housekeeping
+
+Let's set ourselves up with some packages, themes and utility functions.
 
 ```{r}
+# Packages
 library(readr)
@@
 library(tidyr)
+library(gender)
+library(stringr)
+library(lubridate)
+library(highcharter)
 
-films = read_csv("https://raw.githubusercontent.com/TMBish/lab_posts/master/01_actor_careers/00_full_film_data.csv") %>%
-  filter(!is.na(title))
+# Rmarkdown Options
+knitr::opts_chunk$set(echo = TRUE, warning=FALSE, message=FALSE)
+
+# Convert an R vector to string JS vector
+convert_js_vec = function(vec) {
+  js_string = vec %>% round(4) %>% paste(collapse = ",")
+  return(JS( paste0("[", js_string, "]") ))
+}
+
+# Highcharts theme
+source()
+tmbish = high_tmbish()
+```
+
+# Data
+
+I started with imdb user **hagennelson's** list of [top 1000 actors](http://www.imdb.com/list/ls058011111/) and other imdb user **earthanime's** list of [top 250 directors](http://www.imdb.com/list/ls062419846/).
+Both lists span across generations, from the ancient (Ethel Barrymore and Alfred Hitchcock) to the modern (Chloë Grace Moretz and Christopher Nolan).
+
+I then developed code (which I'll cover in a different post) to scrape data from the rotten tomatoes pages of the above individuals' films.
+The final dataset includes **12,258** films and **1,233** indviduals.
+
+Altough we'll only use a few of these variables I brought in a few extras for some future investigations:
+
+Variable | Description
+-------- | -----------
+url | URL extension on rotten tomatoes website
+year | Film production year
+title | Film title
+reviews | Count of formal critic reviews of film
+tomatometer | Percentage of favourable reviews
+av_rating | Average rating of film out of 10
+audience | The non-critic plebian equivolent of the tomatometer
+box_office | The box-office revenue
+director | The film's director
+actor_1:actor_6 | The 6 top actors according to rotten tomatoes internal ranking (seems like screen time)
+
+## Film Data
+
+We'll load and take a peek at the film dataset:
+
+```{r}
+
+films = read_csv("https://raw.githubusercontent.com/TMBish/lab_posts/master/01_actor_careers/00_full_film_data.csv") %>% filter(!is.na(title))
 
@@
 
-### Actors / Directors
+## Individual Data
+
+Now we'll load the individual data.
+
+Unfortunately, because the Rotten Tomatoes devs are a bunch of politically correct SJWs, gender isn't provided on their film bio pages so we'll have to be creative.
+The `gender` package in R allows you to infer a person's gender from their first name and DOB.
+The result is a probabilistic best guess of that individuals most likely gender given their first name and DOB.
 
@@
 # 
+# # Clean some data quality issues on the DOB
 # film_folk[film_folk$dob < as.Date("1880-01-01"), "dob"] = as.Date("1880-01-01")
@@
 
-We should sense check the gender mapping. Let's take a random 10 people to check:
+We should sense check the gender mapping. Let's take a random 10 people to check is working as desired:
 
 ```{r}
+set.seed(123)
+
 genders %>%
@@
 
-Looks pretty, pretty, pretty good.
+Things get dicey with a name like Sandy; however, the package obviously knows that most Sandys born in 1937 were female so we'll have to trust it here.
+Otherwise the list looks pretty, pretty, pretty good.
 
@@
 
-## Gender Gap
+# Q1. Gender Gap
 
-Some text.
-Some text.
-Some text.
-Some text.Some text.
-Some text.
-Some text.
-Some text.
-Some text.
-Some text.
-Some text.
+To answer this question we'll first need to calculate a person's age at the time of their appearance in a film. We'll then
 
 ```{r}
-library(highcharter)
-tmbish = 
-  hc_theme(
-    chart = list(
-      backgroundColor = list("white"),
-      style = list(
-        fontFamily = "Droid Sans"
-      )
-    ),
-    colors = list("#414141", "#FF6A5C", "#CCDFC8", "#056571"),
-    title = list(
-      style = list(fontWeight = "bold", color = "#414141"),
-      align = "left"
-    ),
-    xAxis = list(
-      gridLineColor = "#2196F3",
-      lineColor = "#2196F3",
-      gridLineWidth = 0.5,
-      lineWidth = 0,
-      title = list(style = list(fontWeight = "bold"))
-    ),
-    yAxis = list(
-      gridLineColor = "#2196F3",
-      lineColor = "#2196F3",
-      gridLineWidth = 0.5,
-      lineWidth = 0,
-      title = list(style = list(weight = "bold"))
-    ),
-    subtitle = list(
-      style = list(fontStyle = "italic", color ="#414141"), 
-      align = "left"
-    ),
-    tooltip = list(
-      borderWidth = 0,
-      shape = "square",
-      valueDecimals = 2
-    )
-  )
 
+# Chain a bunch of data wrangling operations
 volume_data =
@@
   ) %>%
-  filter(between(age_at_production, 10,100)) %>%
-  select(name, gender, dob_year, age_at_production, year, role, tomatometer)
-
-  temp = 
-    volume_data %>%
   filter(
+    between(age_at_production, 10,100),
     !is.na(gender)
   ) %>%
+  select(name, gender, dob_year, age_at_production, year, role, tomatometer) %>%
   mutate(
@@
   group_by(category, age_at_production) %>%
-    summarise(films = n()) %>%
+  summarise(
+    films = n()
+  ) %>%
   group_by(category) %>%
-    mutate(percentage = films / sum(films))
+  mutate(
+    percentage = films / sum(films)
+  )
 
@@
 ```{r}
+
+# Shape data for presentation
 chart_data = 
-temp %>%
+  volume_data %>%
   select(-films) %>%
@@
 
-convert_js_vec = function(vec) {
-
-  js_string = vec %>% round(4) %>% paste(collapse = ",")
-
-  return(JS( paste0("[", js_string, "]") ))
-
-}
-
 # For the javascript client side interactivity on the age series chart
@@
 
-chart = 
+# Create chart
+age_dist_chart = 
   highchart() %>%
@@
 
-chart
+age_dist_chart
 ```
@@
 
-<button id = "update_age_series"> Show Cumulative Distribution </button>
+<button class="button secondary outline" id = "update_age_series"> Show Cumulative Distribution </button>
+
+# Q2. Acting and Directing as a skill
+
+> Hypothesis 2: acting and directing skills aren't tied to a person's physical attributes so shouldn't experience deterioration in age.
+In fact you would expect these artists to improve their skills with age.
 
@@
 To investigate our hypothesis we must make a couple of assumptions.
-Since we don't have an individual actor / director performance (like we would have for players in a sporting contest for example) we'll have to assume an actor or director can have a tangible affect on the quality of the movie they appear in; there are obviously many other factors but this seems like a relatively safe assumption.
+Since we don't have an individual actor / director performance (like we have in sports) we'll have to assume an actor or director can have a tangible affect on the quality of the movie they appear in; there are obviously many other factors but this seems like a relatively safe assumption.
 
 Further - for actors - we'll have to limit the dataset to actors that played an important role in the film.
-They  need to be prominent enough so as to affect the overall quality of the film.
-So while Michael Cera's cameo in *This is the End* was quality it can't be said that he influenced the rotten tomatoes rating of the film on his own.
+To implement an `actor performance == film quality` approach the actors need to be prominent enough so as to be able to affect the overall quality of the film.
+So while Michael Cera's cameo in **This is the End** was high quality it can't be said that he influenced the rotten tomatoes rating of the film on his own.
 
@@
 
-After looking through a few rotten tomatoes pages it seems limiting to the top 3 actors in a given film is a good rule of thumb for at least partially influncial performances.
+After looking through a few rotten tomatoes pages it seems limiting to the top 3 actors in a given film is a reasonable cut-off for influncial performances.
 
-### Average Performance by Age
+> INSERT EXAMPLES FROM A FEW ROTTEN TOMATOES PAGES
 
-## Housekeeping
+## Methodology
+
+For every person in the dataset we follow the following recipe:
+
+1. Produce a dataset for each actor with films that:
++ We have a tomatometer score for
++ And the actor is in the top 3 of rotten tomatoes credits
+2. Calculate the `mean` tomatometer for all of this person's films;
+3. Calculate the age the person was at the release of each film;
+4. For every film calculate what `percentage %` this tomato rating is above or below this person's `mean` (called a tomato index)
+
+Producing a dataset like this:
+
+```{r echo=FALSE}
+films %>% 
+  select(title, year, tomatometer, director, actor_1:actor_3) %>%
+  gather("role", "name", director, actor_1:actor_3) %>%
+  inner_join(film_folk) %>%
+  filter(
+    name == "Denzel Washington"
+  ) %>%
+  mutate(
+    age_at_production = year - dob_year
+  ) %>%
+  filter(between(age_at_production, 15,85)) %>%
+  select(title, name, year, gender, age_at_production, tomatometer) %>%
+  group_by(name) %>% 
+  mutate(
+    average_tomato  = round(mean(tomatometer))
+  ) %>% 
+  ungroup() %>%
+  mutate(
+    tomato_index = tomatometer / average_tomato
+  ) %>%
+  arrange(age_at_production) %>%
+  select(title, name, year, age_at_production, tomatometer, average_tomato, tomato_index) %>%
+  mutate(index = scales::percent(tomato_index)) %>%
+  sample_n(10) %>%
+  knitr::kable()
+
+```
+
+## Results
+
+```{r}
+# 
+rating_set =
+  films %>% 
+  select(title, year, tomatometer, director, actor_1:actor_3) %>%
+  gather("role", "name", director, actor_1:actor_3) %>%
+  inner_join(film_folk) %>%
+  filter(!is.na(gender)) %>%
+  mutate(
+    age_at_production = year - dob_year,
+    category = case_when(
+      role == "director" ~ "director",
+      gender == "male" ~ "male_actor",
+      TRUE ~ "female_actor"
+    )
+  ) %>%
+  filter(between(age_at_production, 15,85)) %>%
+  select(name, gender, age_at_production, category, tomatometer) %>%
+  group_by(name) %>% 
+  mutate(
+    average_tomato  = median(tomatometer),
+    films = n()
+  ) %>% ungroup() %>%
+  filter(films >= 5)
+
+rating_volumes = 
+  rating_set %>%
+  group_by(age_at_production) %>%
+  summarise(films = -1*n())
+
+rating_scores = 
+  rating_set %>%
+  mutate(
+    tomato_index = tomatometer / average_tomato) %>%
+  group_by(category, age_at_production) %>%
+  summarise(rating = median(tomato_index)) %>%
+  spread(category, rating)
+
+# LOESS Trend Line
+loess_fit = loess(value ~ age_at_production , 
+                  data = rating_scores %>% gather("role", "value", -age_at_production)
+                  # %>% group_by(age_at_production) %>% summarise(value = mean(value, na.rm = TRUE))
+)
+
+predictions = loess_fit %>% predict(seq(15,85))
+
+volume_chart = 
+  highchart() %>%
+  hc_add_theme(tmbish) %>%
+  hc_chart(height = "300") %>%
+  hc_xAxis(categories = rating_volumes$age_at_production, opposite = TRUE) %>%
+  hc_yAxis(
+    title = list(text = "Total Films in Dataset"),
+    labels = list(formatter = JS("function(){return(-1 * this.value)}"))    
+    ) %>%
+  hc_title(text = "") %>%
+  hc_add_series(
+    name = "Volumes",
+    type = "area",
+    data = rating_volumes$films,
+    marker = list(enabled = FALSE)
+  ) %>% 
+  hc_legend(enabled = FALSE)
+
+rating_chart = 
+  highchart() %>%
+  hc_add_theme(tmbish) %>%
+  hc_chart(
+    animation = list(duration = 2000)
+  ) %>%
+  hc_xAxis(
+    categories = rating_scores$age_at_production,
+    title = list(text = "Age at Production")
+  ) %>%
+  hc_yAxis(
+    title = list(text = "Probablity Density"),
+    min = 0.6
+  ) %>%
+  hc_title(text = "Female actors") %>%
+  hc_subtitle(text = "Comparing male actors, (male) directors and female actors") %>%
+  hc_add_series(
+    name = "Director",
+    type = "scatter",
+    data = rating_scores$director,
+    marker = list(radius = 3, symbol = "circle")
+  ) %>%
+  hc_add_series(
+    name = "Male Actor",
+    type = "scatter",
+    data = rating_scores$male_actor,
+    marker = list(radius = 3, symbol = "circle")
+  ) %>%
+  hc_add_series(
+    name = "Female Actor",
+    type = "scatter",
+    data = rating_scores$female_actor,
+    marker = list(radius = 3, symbol = "circle")
+  ) %>%
+  hc_add_series(
+    name = "Trend",
+    type = "spline",
+    data = predictions,
+    color = "#000000",
+    marker = list(enabled = FALSE)
+  )
+
+```
+
+```{r echo = FALSE}
+chart
+```
+
+```{r echo = FALSE}
+volume_chart
+```
 
@@
 $("#update_age_series").html("Show Density");
+
 };

### 2017-08-22 01_actor_careers/04_analyse.R

@@ -12,7 +12,7 @@ films = read_csv("https://raw.githubusercontent.com/TMBish/lab_posts/master/01_a
   filter(!is.na(title))
 
 
-film_folk = read_csv("https://raw.githubusercontent.com/TMBish/lab_posts/master/01_actor_careers/00_actors_directors.csv")
+film_folk=read_csv("https://raw.githubusercontent.com/TMBish/lab_posts/master/01_actor_careers/00_actors_directors.csv")
 film_folk[film_folk$dob < as.Date("1880-01-01"), "dob"] = as.Date("1880-01-01")
 
 # Grep out first name and dob year for the gender function
@@ -33,6 +33,8 @@ genders =
 film_folk = 
   film_folk %>%
   left_join(genders)
+
+x = 19
 
  # The deal with directors? --------------------------------------------------------------------
 dir_data =
@@ -75,43 +77,6 @@ volume_data =
 	ggplot(data = temp) +
 		geom_bar(aes(x = age_at_production)) +
 		facet_grid(gender ~ .)
-
-	# Highcharts
-	var = "Actor"
-	temp = 
-		volume_data %>%
-		filter(
-			role == var,
-			!is.na(gender)
-		) %>%
-		group_by(gender, age_at_production) %>%
-		summarise(films = n()) %>%
-		group_by(gender) %>%
-		mutate(percentage = films / sum(films))
-
-	chart = hchart(temp, "column", hcaes(x = age_at_production, y = percentage, group = gender)) %>%
-  		hc_add_theme(tmbish)
-
-  	# Including directors as a category
-	temp = 
-		volume_data %>%
-		filter(
-			!is.na(gender)
-		) %>%
-		mutate(
-			category = case_when(
-				role == "Director" ~ "director",
-				gender == "male" ~ "male_actor",
-				TRUE ~ "female_actor"
-			)
-		) %>% 
-		group_by(category, age_at_production) %>%
-		summarise(films = n()) %>%
-		group_by(category) %>%
-		mutate(percentage = films / sum(films))
-
-	chart = hchart(temp, "spline", hcaes(x = age_at_production, y = percentage, group = category)) %>%
-  		hc_add_theme(tmbish)
 
   	# PDF
   	chart_data = 
@@ -248,7 +213,6 @@ chart =
     type = "scatter",
     data = rating_data$female_actor,
     marker = list(radius = 3, symbol = "circle")
-    
     ) %>%
   hc_add_series(
[…]

### 2017-08-22 highcharts_theme.R

@@ -1,0 +1,42 @@
+high_tmbish = function() {
+  
+  out = 
+    hc_theme(
+      chart = list(
+        backgroundColor = list("white"),
+        style = list(
+          fontFamily = "Droid Sans"
+        )
+      ),
+      colors = list("#414141", "#FF6A5C", "#CCDFC8", "#056571"),
+      title = list(
+        style = list(fontWeight = "bold", color = "#414141"),
+        align = "left"
+      ),
+      xAxis = list(
+        gridLineColor = "#2196F3",
+        lineColor = "#2196F3",
+        gridLineWidth = 0.5,
+        lineWidth = 0,
+        title = list(style = list(fontWeight = "bold"))
+      ),
+      yAxis = list(
+        gridLineColor = "#2196F3",
+        lineColor = "#2196F3",
+        gridLineWidth = 0.5,
+        lineWidth = 0,
+        title = list(style = list(weight = "bold"))
+      ),
+      subtitle = list(
+        style = list(fontStyle = "italic", color ="#414141"), 
+        align = "left"
+      ),
+      tooltip = list(
+        borderWidth = 0,
+        shape = "square",
+        valueDecimals = 2
+      )
+    )
+  
+}
+  

### 2017-08-23 highcharts_theme.R
added some sauce

@@ -3,29 +3,29 @@ high_tmbish = function() {
   out = 
     hc_theme(
       chart = list(
-        backgroundColor = list("white"),
+        backgroundColor = "#FDFFFC",
         style = list(
-          fontFamily = "Droid Sans"
+          fontFamily = "Grand Hotel"
         )
       ),
-      colors = list("#414141", "#FF6A5C", "#CCDFC8", "#056571"),
+      colors = list("#FF9F1C", "#2EC4B6", "#FE5F55", "#FE5F55"),
       title = list(
         style = list(fontWeight = "bold", color = "#414141"),
         align = "left"
       ),
       xAxis = list(
-        gridLineColor = "#2196F3",
-        lineColor = "#2196F3",
-        gridLineWidth = 0.5,
-        lineWidth = 0,
+        gridLineColor = "#011627",
+        lineColor = "#011627",
+        gridLineWidth = 0.1,
+        lineWidth = 1,
         title = list(style = list(fontWeight = "bold"))
       ),
       yAxis = list(
-        gridLineColor = "#2196F3",
-        lineColor = "#2196F3",
-        gridLineWidth = 0.5,
-        lineWidth = 0,
-        title = list(style = list(weight = "bold"))
+        gridLineColor = "#011627",
+        lineColor = "#011627",
+        gridLineWidth = 0.1,
+        lineWidth = 1,
+        title = list(style = list(fontWeight = "bold"))
       ),
       subtitle = list(
         style = list(fontStyle = "italic", color ="#414141"), 
@@ -35,8 +35,29 @@ high_tmbish = function() {
         borderWidth = 0,
         shape = "square",
         valueDecimals = 2
+      ),
+      plotOptions = list(
+        line = list(marker = list(symbol = "circle", lineWidth = 2, radius = 5)),
+        spline = list(marker = list(symbol = "circle", lineWidth = 2, radius = 5))
+      ),
+      legend = list(
+        align = "right",
+        # floating = TRUE,
+        layout = "vertical",
+        backgroundColor = "#FFF",
+        shadow = TRUE,
+        title = "Legend",
+        verticalAlign = "middle"
+      ),
+      exporting = list(
+        enabled = TRUE
+      ),
+      credits = list(
+        enabled = TRUE,
+        href = "https://github.com/TMBish/lab_posts/blob/master/highcharts_theme.R",
+        text = "My schmick highcharts theme"
       )
+      
     )
   
 }
-  

### 2017-08-23 highcharts_theme.R
Gridlines

@@ -14,18 +14,19 @@ high_tmbish = function() {
         align = "left"
       ),
       xAxis = list(
-        gridLineColor = "#011627",
-        lineColor = "#011627",
-        gridLineWidth = 0.1,
-        lineWidth = 1,
+        lineWidth = 1, lineColor = "#011627",
+        gridLineWidth = 0.2, gridLineColor = "#011627", gridLineDashStyle = "LongDash",
         title = list(style = list(fontWeight = "bold"))
       ),
       yAxis = list(
-        gridLineColor = "#011627",
-        lineColor = "#011627",
-        gridLineWidth = 0.1,
-        lineWidth = 1,
-        title = list(style = list(fontWeight = "bold"))
+        lineWidth = 1, lineColor = "#011627",
+        gridLineWidth = 0.2, gridLineColor = "#011627", gridLineDashStyle = "LongDash",
+        minorGridLineWidth = 0.1, minorGridLineColor = "#011627",
+        title = list(style = list(fontWeight = "bold")),
+        tickColor = "#011627",
+        tickLength = 10,
+        minorTickLength = 5, minorTickWidth = 1
+        
       ),
       subtitle = list(
         style = list(fontStyle = "italic", color ="#414141"), 
@@ -57,7 +58,6 @@ high_tmbish = function() {
         href = "https://github.com/TMBish/lab_posts/blob/master/highcharts_theme.R",
         text = "My schmick highcharts theme"
       )
-      
     )
-  
 }
+

### 2017-08-26 01_actor_careers/05_report.Rmd
theme update

@@
 
+# For reproducibility
+set.seed(123)
+
 # Convert an R vector to string JS vector
@@
 # Highcharts theme
-source()
+source("https://raw.githubusercontent.com/TMBish/lab_posts/master/highcharts_theme.R")
 tmbish = high_tmbish()
@@
 ```{r}
-
+# Load in films data from Github Repo
 films = read_csv("https://raw.githubusercontent.com/TMBish/lab_posts/master/01_actor_careers/00_full_film_data.csv") %>% filter(!is.na(title))
@@
 
-# library(gender)
-# library(stringr)
-# library(lubridate)
-# 
-# film_folk = read_csv("https://raw.githubusercontent.com/TMBish/lab_posts/master/01_actor_careers/00_actors_directors.csv")
-# 
-# # Clean some data quality issues on the DOB
-# film_folk[film_folk$dob < as.Date("1880-01-01"), "dob"] = as.Date("1880-01-01")
-# 
-# # Grep out first name and dob year for the gender function
-# film_folk =
-#   film_folk %>%
-#   mutate(
-#     first_name = str_extract(name, "(?i)[a-z]+(?=\\s)"),
-#     dob_year = year(dob)
-#   )
-# 
-# # Distinct name, dob combos and predict gender
-# genders =
-#   film_folk %>%
-#   distinct(first_name, dob_year) %>%
-#   gender_df(name_col = "first_name", year_col = "dob_year") %>%
-#   select("first_name" = name, gender, "dob_year" = year_min)
+library(gender)
+library(stringr)
+library(lubridate)
+
+film_folk = read_csv("https://raw.githubusercontent.com/TMBish/lab_posts/master/01_actor_careers/00_actors_directors.csv")
+
+# Clean some data quality issues on the DOB
+film_folk[film_folk$dob < as.Date("1880-01-01"), "dob"] = as.Date("1880-01-01")
+
+# Grep out first name and dob year for the gender function
+film_folk =
+  film_folk %>%
+  mutate(
+    first_name = str_extract(name, "(?i)[a-z]+(?=\\s)"),
+    dob_year = year(dob)
+  )
+
+# Distinct name, dob combos and predict gender
+genders =
+  film_folk %>%
+  distinct(first_name, dob_year) %>%
+  gender_df(name_col = "first_name", year_col = "dob_year") %>%
+  select("first_name" = name, gender, "dob_year" = year_min)
 
@@
 
-We should sense check the gender mapping. Let's take a random 10 people to check is working as desired:
+We should sense check the gender mapping to make sure the package is making logical inferences. Let's take a random 10 person sample:
 
 ```{r}
-set.seed(123)
-
 genders %>%
   sample_n(10) %>%
-  knitr::kable(caption = "Sense Checking the Gender Mapping")
-
+  knitr::kable()
 ```
 
-Things get dicey with a name like Sandy; however, the package obviously knows that most Sandys born in 1937 were female so we'll have to trust it here.
-Otherwise the list looks pretty, pretty, pretty good.
+So generally this is looking pretty, pretty good.
+Things get dicey with unisex names like Sandy; however, the package must know that most Sandys born in 1937 were female so we'll have to trust it here.
+Finally we'll need to join this information back to the individual data set.
 
@@
 
-# Q1. Gender Gap
+# Female Directors?
 
-To answer this question we'll first need to calculate a person's age at the time of their appearance in a film. We'll then
+# How old?
+
+We've finally sorted out our source data.
+However, we still need to add a few variables to be able to answer this question.
+We need we'll first need to calculate a person's age at the time of their appearance in a film.
+We'll then
 
@@
 ```{r echo = FALSE}
-chart
+rating_chart
 ```

### 2017-08-26 01_actor_careers/04_analyse.R

@@ -80,9 +80,9 @@ volume_data =
 
   	# PDF
   	chart_data = 
-   temp %>%
-    select(-films) %>%
-    spread(category, percentage)
+     temp %>%
+      select(-films) %>%
+      spread(category, percentage)
 
 	chart = 
 	  highchart() %>%
@@ -174,7 +174,8 @@ rating_data =
 
 # LOESS Trend Line
 loess_fit = loess(value ~ age_at_production , 
-                  data = rating_data %>% gather("role", "value", -age_at_production)
+                  data = rating_data %>% gather("role", "value", -age_at_production),
+                  span = 0.6
                   # %>% group_by(age_at_production) %>% summarise(value = mean(value, na.rm = TRUE))
                   )
 	

### 2017-08-26 highcharts_theme.R

@@ -1,32 +1,37 @@
 high_tmbish = function() {
   
+  base_font = "Josefin Slab"
+  header_font = "Arvo"
+  
+  header_style = list(fontFamily = header_font, fontWeight = "bold", color = "#011627")
+  
   out = 
     hc_theme(
       chart = list(
         backgroundColor = "#FDFFFC",
         style = list(
-          fontFamily = "Grand Hotel"
+          fontFamily = base_font
         )
       ),
-      colors = list("#FF9F1C", "#2EC4B6", "#FE5F55", "#FE5F55"),
+      colors = list("#FF9F1C", "#2EC4B6", "#FE5F55", "#C1E1F1", "#5FEF9B"),
       title = list(
-        style = list(fontWeight = "bold", color = "#414141"),
+        style = header_style,
         align = "left"
       ),
       xAxis = list(
         lineWidth = 1, lineColor = "#011627",
         gridLineWidth = 0.2, gridLineColor = "#011627", gridLineDashStyle = "LongDash",
-        title = list(style = list(fontWeight = "bold"))
+        tickWidth = 0,
+        title = list(style = header_style)
       ),
       yAxis = list(
         lineWidth = 1, lineColor = "#011627",
         gridLineWidth = 0.2, gridLineColor = "#011627", gridLineDashStyle = "LongDash",
         minorGridLineWidth = 0.1, minorGridLineColor = "#011627",
-        title = list(style = list(fontWeight = "bold")),
-        tickColor = "#011627",
-        tickLength = 10,
-        minorTickLength = 5, minorTickWidth = 1
-        
+        # tickColor = "#011627",tickLength = 10,
+        # minorTickLength = 5, minorTickWidth = 1,
+        tickWidth = 0,
+        title = list(style = header_style)
       ),
       subtitle = list(
         style = list(fontStyle = "italic", color ="#414141"), 
@@ -35,7 +40,22 @@ high_tmbish = function() {
       tooltip = list(
         borderWidth = 0,
         shape = "square",
-        valueDecimals = 2
+        valueDecimals = 2,
+        backgroundColor = "#FFF",
+        valueDecimals = 2,
+        headerFormat = ""
+        # footerFormat = "<span style = 'background-color: {point.color}; height = 4px; width = 100%;'> </span>"
+        # formatter = JS("function() {
+        #                series = this.series.name;
+        #                x_var = this.series.x;
+        #                x_val = this.x;
+        #                y_var = this.y;
+        #                y_val = this.y
+        #                colour = this.y;
[…]

### 2017-08-27 01_actor_careers/05_report.Rmd
updates

@@
 ---
-title: "Films: Age & Gender"
+title: "The prime of their life - the halflife of acting talent"
 output: 
@@
 
-# Questions?
+> insert an image
 
-Let's say we had a couple of questions about actors and directors:
+Much analysis has been completed regarding the performing peak of athletes and sportspeople.
+Statistically, swimmers peak at around 24, marathoner runners between 30-31, gymnasts at a mere 18, NBA players generally peak between 26-29, professional hockey players between 27-28, and chess players at 30-35.
 
-> Do actors and directors improve with age?
-
-> Are female actors generally cast  than their male counterparts?
-
-To answer these questions we're going to need some data.
+Does the idea of a performing prime extend to artists and specifically actors and directors?
+There are obvious reasons to be skeptical.
+There's no major physical component to acting that could decay as the body does, and unlike chess you wouldn't think there's the need for an exreme state of concentration and cognition which might be unreachable in older age.
+There are other confounding factors that might prevent us from answering this question difinitively (which I'll discuss later) but let's dig into the data.
 
@@
 
-I started with imdb user **hagennelson's** list of [top 1000 actors](http://www.imdb.com/list/ls058011111/) and other imdb user **earthanime's** list of [top 250 directors](http://www.imdb.com/list/ls062419846/).
+To curate a data set for anlaysis I started with imdb user **hagennelson's** list of [top 1000 actors](http://www.imdb.com/list/ls058011111/) and imdb user **earthanime's** list of [top 250 directors](http://www.imdb.com/list/ls062419846/).
 Both lists span across generations, from the ancient (Ethel Barrymore and Alfred Hitchcock) to the modern (Chloë Grace Moretz and Christopher Nolan).
 
-I then developed code (which I'll cover in a different post) to scrape data from the rotten tomatoes pages of the above individuals' films.
+I then developed code (available on GitHub) to scrape data from the rotten tomatoes pages of the above individuals' films.
 The final dataset includes **12,258** films and **1,233** indviduals.
-
-Altough we'll only use a few of these variables I brought in a few extras for some future investigations:
+Although we'll only use a few of these variables, I brought in a few extras for some future investigations:
 
@@
 director | The film's director
-actor_1:actor_6 | The 6 top actors according to rotten tomatoes internal ranking (seems like screen time)
+actor_1:actor_6 | The 6 top actors according to rotten tomatoes internal ranking (seemingly ordered by screen time)
 
@@
 
-We'll load and take a peek at the film dataset:
+First we'll load and take a peek at the film dataset:
 
@@
 films = read_csv("https://raw.githubusercontent.com/TMBish/lab_posts/master/01_actor_careers/00_full_film_data.csv") %>% filter(!is.na(title))
+
+films %>% head()
 
@@
 
-Unfortunately, because the Rotten Tomatoes devs are a bunch of politically correct SJWs, gender isn't provided on their film bio pages so we'll have to be creative.
-The `gender` package in R allows you to infer a person's gender from their first name and DOB.
-The result is a probabilistic best guess of that individuals most likely gender given their first name and DOB.
+Unfortunately, because the Rotten Tomatoes development tea are a bunch of politically correct SJWs, gender isn't provided on their film bio pages so we'll have to be creative.
+The `gender` R package allows you to infer a person's gender from their first name and DOB.
+The result is a probabilistic estimate of that individuals most likely gender given their first name and DOB.
 
@@
 # Grep out first name and dob year for the gender function
-film_folk =
-  film_folk %>%
+film_folk = film_folk %>%
               mutate(
@@
 # Distinct name, dob combos and predict gender
-genders =
-  film_folk %>%
+genders = film_folk %>%
             distinct(first_name, dob_year) %>%
@@
 
-# Female Directors?
+# Where are the female directors?
 
-# How old?
+To add a layer to this analysis I wanted group together people by gender and film production role (or actor vs director).
+So we think we'd be working with 4 groups, however, I was suprised to see that of our 250 top directors only XXX were female which is pretty appaling.
+
+This got me thinking about the rest of the dataset.
+Given our **12,258** films dataset isn't limited to director credits in our top 250 (the film might just have a top 1000 actor appear in it) we can get a bit of a better idea of the broader gender split of directors.
+I've captured a lot of the key numbers in the following chart.
+
+```{r}
+```
+
+# So
 

### 2017-08-28 01_actor_careers/05_report.Rmd
Prose

@@
 Much analysis has been completed regarding the performing peak of athletes and sportspeople.
-Statistically, swimmers peak at around 24, marathoner runners between 30-31, gymnasts at a mere 18, NBA players generally peak between 26-29, professional hockey players between 27-28, and chess players at 30-35.
+Statistically, swimmers peak at around 24, marathon runners between 30-31, gymnasts at a mere 18, NBA players generally peak between 26-29, professional hockey players between 27-28, and chess players at 30-35.
 
-Does the idea of a performing prime extend to artists and specifically actors and directors?
+Does the idea of a performing prime extend to artists, specifically actors and directors?
 There are obvious reasons to be skeptical.
-There's no major physical component to acting that could decay as the body does, and unlike chess you wouldn't think there's the need for an exreme state of concentration and cognition which might be unreachable in older age.
-There are other confounding factors that might prevent us from answering this question difinitively (which I'll discuss later) but let's dig into the data.
+Importantly there's no major physical component to acting that would decay as the body does, and unlike chess you wouldn't think there's the need for an exreme state of concentration and cognition which might be unreachable at older ages.
+
+There are significant confounding factors that might prevent us from answering this question difinitively (which I'll discuss later) but let's dig into the data.
 
@@
 Variable | Description
--------- | -----------
+------------ | ---------------------
 url | URL extension on rotten tomatoes website
@@
 
-# Where are the female directors?
+# What's the deal with female directors?
 
-To add a layer to this analysis I wanted group together people by gender and film production role (or actor vs director).
-So we think we'd be working with 4 groups, however, I was suprised to see that of our 250 top directors only XXX were female which is pretty appaling.
+To add a layer to this analysis I wanted group people by gender and film production role (actor vs director).
+So we think we'd be working with 4 groups, however, I was suprised to see that of our 250 top directors only XXX were female.
+A consequence of history but appaling nonetheless.
 
 This got me thinking about the rest of the dataset.
-Given our **12,258** films dataset isn't limited to director credits in our top 250 (the film might just have a top 1000 actor appear in it) we can get a bit of a better idea of the broader gender split of directors.
+Given our **12,258** films dataset isn't limited to director credits in our top 250 (films in the set are contributed by both actor and director credits) we can get a bit of a better idea of the broader gender split of directors.
 I've captured a lot of the key numbers in the following chart.
@@
 ```{r}
+# Directors
+
+# Top 250
+top250 = films %>%
+          select("name" = director) %>%
+          inner_join(film_folk) %>%
+          group_by(gender) %>%
+          summarise(
+            films = n(),
+            directors = n_distinct(name)
+          )
+
 ```
 
-# So
+# How old are we when we produce films?
 

### 2017-08-29 01_actor_careers/05_report.Rmd
director code added

@@
 This got me thinking about the rest of the dataset.
-Given our **12,258** films dataset isn't limited to director credits in our top 250 (films in the set are contributed by both actor and director credits) we can get a bit of a better idea of the broader gender split of directors.
+Given our **12,258** film dataset isn't limited to director credits in our top 250 (films in the set are contributed by both actor and director credits) we can get a bit of a better idea of the broader gender split of directors.
 I've captured a lot of the key numbers in the following chart.
@@
 ```{r}
+# Establish a persistent dataset of interest
+data = films %>%
+        select(title, year, tomatometer, director:actor_6) %>%
+        gather("role", "name", director:actor_6) %>%
+        inner_join(film_folk) %>%
+        select(-first_name) %>%
+        mutate(
+          role_type = ifelse(role == "director", "Director", "Actor"),
+          age_at_production = year - dob_year,
+          category = case_when(
+            role_type == "Director" ~ "director",
+            gender == "male" ~ "male_actor",
+            gender == "female" ~ "female_actor",
+            TRUE ~ "other"
+          )
+        )
+
 # Directors
 
-# Top 250
-top250 = films %>%
-          select("name" = director) %>%
-          inner_join(film_folk) %>%
-          group_by(gender) %>%
+# Data for known individuals
+known_summary = 
+  data %>%
+  group_by(role_type, gender) %>%
   summarise(
     films = n(),
-            directors = n_distinct(name)
+    distinct_people = n_distinct(name)
   )
+
+# Unknown directors
+unknown_set = films %>%
+          select("name" = director) %>%
+          anti_join(film_folk) %>%
+          mutate(
+            first_name = str_extract(name, "(?i)[a-z]+(?=\\s)"),
+            min_year = 1900, max_year = 1980
+          ) %>%
+          filter(!is.na(first_name))
+
+unknown_genders = 
+  unknown_set %>% 
+  gender_df(name_col = "first_name", year_col = c("min_year", "max_year")) %>%
+  select("first_name" = name, gender)
+
+unknown_summary = 
+  unknown_set %>%
+  inner_join(unknown_genders) %>%
+  mutate(role_type = "Director (Non Top250)") %>%
+  group_by(role_type, gender) %>%
+  summarise(
+    films = n(),
+    distinct_people = n_distinct(name)
+  )
+
+chart_data = 
+  known_summary %>%
+  union_all(unknown_summary) %>%
+  group_by(role_type) %>%
+  mutate(
+    films_prop = films / sum(films),
+    people_prop = distinct_people / sum(distinct_people)
+  ) %>% ungroup()
+
+map(c("Actor", "Director", "Director (Non Top250)"), function(x) {
+
+    chart_data %>%
+    filter(role_type == x) %>%
+    gather("variable", "value", films_prop, people_prop) %>%
+    hchart(hcaes(x = gender, group = variable, y = value)) %>%
+    hc_title(text = x)
+
+}) %>%
+hw_grid(ncol = 1) %>% 
+browsable()
 

### 2017-08-30 01_actor_careers/05_report.Rmd
mapper

@@
   union_all(unknown_summary) %>%
-  group_by(role_type) %>%
-  mutate(
-    films_prop = films / sum(films),
-    people_prop = distinct_people / sum(distinct_people)
-  ) %>% ungroup()
+  filter(!is.na(gender))
 
-map(c("Actor", "Director", "Director (Non Top250)"), function(x) {
+map(c("films", "distinct_people"), function(x) {
 
+    data = 
       chart_data %>%
-    filter(role_type == x) %>%
-    gather("variable", "value", films_prop, people_prop) %>%
-    hchart(hcaes(x = gender, group = variable, y = value)) %>%
-    hc_title(text = x)
+      select_("role_type", "gender", x) %>%
+      spread_("gender", x, fill = 0)
+
+    base = highchart() %>%
+            hc_chart(type = "column") %>%
+            hc_add_theme(tmbish) %>%
+            hc_xAxis(categories = data$role_type) %>%
+            hc_plotOptions(
+              column = list(
+                stacking = 'percent',
+                dataLabels = list(
+                  enabled = TRUE
+                  #,formatter = JS("function(){ return(point.percentage)}")
+                )
+              )
+            ) %>%
+            hc_title(text = ifelse(x=="films", "By Volume of Films", "By Distinct Individuals"))
+
+    for (i in c("female", "male")) {
+      base = base %>% hc_add_series(name = i, data = data[,i] %>% unlist() %>% as.integer())
+    }
+
+    if (x == "films") { base  = base %>% hc_legend(enabled=FALSE)}
+
+    return(base)
 
 }) %>%
-hw_grid(ncol = 1) %>% 
+hw_grid(ncol = 2) %>% 
 browsable()

### 2017-08-30 01_actor_careers/05_report.Rmd
updated theme

--- 2017-08-28 01_actor_careers/05_report.Rmd
@@
 
-# Housekeeping
+```{r echo = FALSE, warning=FALSE, message=FALSE}
+# Let's set ourselves up with some packages, themes and utility functions.
 
-Let's set ourselves up with some packages, themes and utility functions.
-
-```{r}
 # Packages
@@
 library(highcharter)
+library(purrr)
+library(htmltools)
 
 # Rmarkdown Options
-knitr::opts_chunk$set(echo = TRUE, warning=FALSE, message=FALSE)
+knitr::opts_chunk$set(echo = FALSE, warning=FALSE, message=FALSE)
 
@@
 
-First we'll load and take a peek at the film dataset:
-
+Let's have a look at the films data set
 ```{r}
@@
 
-films %>% head()
+films %>% 
+  select(-url) %>%
+  sample_n(5) %>%
+  knitr::kable()
 
@@
 
-Unfortunately, because the Rotten Tomatoes development tea are a bunch of politically correct SJWs, gender isn't provided on their film bio pages so we'll have to be creative.
+Unfortunately, because the Rotten Tomatoes development team are a bunch of politically correct SJWs, gender isn't provided on their film bio pages so we'll have to be creative.
 The `gender` R package allows you to infer a person's gender from their first name and DOB.
@@
 To add a layer to this analysis I wanted group people by gender and film production role (actor vs director).
-So we think we'd be working with 4 groups, however, I was suprised to see that of our 250 top directors only XXX were female.
+So we think we'd be working with 4 groups, however, I was suprised to see that of our 250 top directors only 25 were female.
 A consequence of history but appaling nonetheless.
@@
 This got me thinking about the rest of the dataset.
-Given our **12,258** films dataset isn't limited to director credits in our top 250 (films in the set are contributed by both actor and director credits) we can get a bit of a better idea of the broader gender split of directors.
+Given our **12,258** film dataset isn't limited to director credits in our top 250 (films in the set are contributed by both actor and director credits) we can get a bit of a better idea of the broader gender split for film directors.
 I've captured a lot of the key numbers in the following chart.
@@
 ```{r}
+# Establish a persistent dataset of interest
+master = films %>%
+        select(title, year, tomatometer, director:actor_6) %>%
+        gather("role", "name", director:actor_6) %>%
+        inner_join(film_folk) %>%
+        select(-first_name) %>%
+        mutate(
+          role_type = ifelse(role == "director", "Director", "Actor"),
+          age_at_production = year - dob_year,
+          category = case_when(
+            role_type == "Director" ~ "director",
+            gender == "male" ~ "male_actor",
+            gender == "female" ~ "female_actor",
+            TRUE ~ "other"
+          )
+        )
+
 # Directors
 
-# Top 250
-top250 = films %>%
-          select("name" = director) %>%
-          inner_join(film_folk) %>%
-          group_by(gender) %>%
+# Data for known individuals
+known_summary = 
+  master %>%
+  group_by(role_type, gender) %>%
   summarise(
     films = n(),
-            directors = n_distinct(name)
+    distinct_people = n_distinct(name)
   )
+
+# Unknown directors
+unknown_set = films %>%
+          select("name" = director) %>%
+          anti_join(film_folk) %>%
+          mutate(
+            first_name = str_extract(name, "(?i)[a-z]+(?=\\s)"),
+            min_year = 1900, max_year = 1980
+          ) %>%
+          filter(!is.na(first_name))
+
+unknown_genders = 
+  unknown_set %>% 
+  gender_df(name_col = "first_name", year_col = c("min_year", "max_year")) %>%
+  select("first_name" = name, gender)
+
+unknown_summary = 
+  unknown_set %>%
+  inner_join(unknown_genders) %>%
+  mutate(role_type = "Director (Non Top250)") %>%
+  group_by(role_type, gender) %>%
+  summarise(
+    films = n(),
+    distinct_people = n_distinct(name)
+  )
+
+chart_data = 
+  known_summary %>%
+  union_all(unknown_summary) %>%
+  filter(!is.na(gender))
+
+gender_props = list()
+
+for (metric in c("films", "distinct_people")) {
+
+  data = 
+        chart_data %>%
+        select_("role_type", "gender", metric) %>%
+        spread_("gender", metric, fill = 0)
+
+    base_chart = 
+      highchart() %>%
+      hc_chart(type = "column") %>%
+      hc_add_theme(tmbish) %>%
+      hc_xAxis(categories = data$role_type) %>%
+      hc_plotOptions(
+        column = list(
+          stacking = 'percent',
+          dataLabels = list(
+            enabled = TRUE,
+            color = "#FFF",
+            style = list(textOutline = NULL, fontSize = "14px"),
+            formatter = JS("function(){ return(Math.round(this.percentage) + '%')}")
+          )
+        )
+      ) %>%
+      hc_title(text = ifelse(metric=="films", "By Volume of Films", "By Distinct Individuals")) %>%
+      hc_legend(align = "center", verticalAlign = "bottom", layout = "horizontal")
+
+    for (i in c("female", "male")) {
+      base_chart = base_chart %>% hc_add_series(name = i, data = data[,i] %>% unlist() %>% as.integer())
+    }
+
+    if (metric != "films") { base_chart  = base_chart %>% hc_legend(enabled=FALSE)}
+
+  gender_props[[metric]] = base_chart
+
+}
+
+gender_props %>%
+  hw_grid(ncol = 1, rowheight = "400px") %>%
+  browsable()
 
@@
 
-# How old are we when we produce films?
+> Insert finding graphic thing
 
-We've finally sorted out our source data.
-However, we still need to add a few variables to be able to answer this question.
-We need we'll first need to calculate a person's age at the time of their appearance in a film.
-We'll then
+So henceforth we'll treat directors as a single bloc and you can assume that they're male statistically speaking.
+
+# I starred in or directed a film; how old am I likely to be?
+
+Well, as it turns out, it depends.
+We'll group individuals in groups: directors (predominantly male as seen above), male actors, and female actors.
+For all these individuals we calculate their age at the time a film they were in was realeased and plot the densities within each group.
+
+Switch between the denisty (proportion appearing at one speicific age) and cumulative distribution (proportion appearing at **or before** at specific age) views to better understand the data.
 
@@
 volume_data =
-  films %>% 
-  select(title, year, tomatometer, director, actor_1:actor_6) %>%
-  gather("role", "name", director, actor_1:actor_6) %>%
-  mutate(role = ifelse(role == "director", "Director", "Actor")) %>%
-  inner_join(film_folk) %>%
-  mutate(
-    age_at_production = year - dob_year
-  ) %>%
+  master %>%
   filter(
     between(age_at_production, 10,100),
-    !is.na(gender)
-  ) %>%
-  select(name, gender, dob_year, age_at_production, year, role, tomatometer) %>%
-  mutate(
-    category = case_when(
-      role == "Director" ~ "director",
-      gender == "male" ~ "male_actor",
-      TRUE ~ "female_actor"
-    )
+    !is.na(gender),
+    category != "other"
   ) %>%
@@
   ) %>%
-  hc_title(text = "Female actors") %>%
-  hc_subtitle(text = "Comparing male actors, (male) directors and female actors") %>%
+  hc_title(text = "Age at Production") %>%
+  hc_subtitle(text = "Comparing the distribution of film professionals for age at the time of film productions") %>%
   hc_add_series(
@@
     name = "Female Actor",
-    type = "area",
+    type = "spline",
     data = chart_data$female_actor,
-    zIndex = -10,
-    marker = list(enabled = FALSE),
-    fillOpacity = 0.5
+    zIndex = -10
+    #marker = list(enabled = FALSE)
+    #fillOpacity = 0.5
   )
@@
 
-# Q2. Acting and Directing as a skill
+> Insert infographic thing
+
+# The half life of acting talent
 
@@
 
-To investigate our hypothesis we must make a couple of assumptions.
-Since we don't have an individual actor / director performance (like we have in sports) we'll have to assume an actor or director can have a tangible affect on the quality of the movie they appear in; there are obviously many other factors but this seems like a relatively safe assumption.
+To investigate this hypothesis we must make a couple of assumptions.
+Since we don't have individual actor / director performance metrics (like we have in sports) we'll have to assume an actor or director can have a material affect on the quality of the movie they appear in; there are obviously many other factors but this seems like a relatively safe assumption.
 
 Further - for actors - we'll have to limit the dataset to actors that played an important role in the film.
-To implement an `actor performance == film quality` approach the actors need to be prominent enough so as to be able to affect the overall quality of the film.
+To implement an `actor performance == film quality` approach the actors need to be noteworthy enough to be able to affect the overall quality of the film.
 So while Michael Cera's cameo in **This is the End** was high quality it can't be said that he influenced the rotten tomatoes rating of the film on his own.
@@
 
-For every person in the dataset we follow the following recipe:
+There's a few other things we want to control for here.
+I don't want to plot raw film critical rating because we might be prone to idiosyncracies of groups or ages - high performing directors might generally wait until they feel experienced enough to direct their first film as an example.
 
-1. Produce a dataset for each actor with films that:
-+ We have a tomatometer score for
-+ And the actor is in the top 3 of rotten tomatoes credits
-2. Calculate the `mean` tomatometer for all of this person's films;
-3. Calculate the age the person was at the release of each film;
-4. For every film calculate what `percentage %` this tomato rating is above or below this person's `mean` (called a tomato index)
+Instead we'll plot, for each individual and film, how well they have perfomed relative to that individual's mean lifetime score (the average tomatometer of all that individual's films).
+This gives us a common scale on which to compare.
 
-Producing a dataset like this:
+To illustrate this approach let's look at Denzel Washington's films. Denzel has a healthy mean tomatometer of 68%.
 
 ```{r echo=FALSE}
-films %>% 
-  select(title, year, tomatometer, director, actor_1:actor_3) %>%
-  gather("role", "name", director, actor_1:actor_3) %>%
-  inner_join(film_folk) %>%
+master %>% 
   filter(
-    name == "Denzel Washington"
+    !(role %in% c("actor_4","actor_5", "actor_6")),
+    name == "Denzel Washington",
+    between(age_at_production, 15,85)
   ) %>%
-  mutate(
-    age_at_production = year - dob_year
-  ) %>%
-  filter(between(age_at_production, 15,85)) %>%
-  select(title, name, year, gender, age_at_production, tomatometer) %>%
   group_by(name) %>% 
@@
   mutate(
-    tomato_index = tomatometer / average_tomato
+    tomato_index = (tomatometer - average_tomato) / average_tomato
   ) %>%
+  sample_n(10) %>%
   arrange(age_at_production) %>%
   select(title, name, year, age_at_production, tomatometer, average_tomato, tomato_index) %>%
-  mutate(index = scales::percent(tomato_index)) %>%
-  sample_n(10) %>%
+  mutate(tomato_index = scales::percent(tomato_index)) %>%
   knitr::kable()
@@
 
+So based on this 10 film sample Denzel had a solid 40s where his films (of the likes **Hurricane** and **Courage Under Fire**) average a rotten tomatoes rating about 20% above his career average.
+He looks like he dropped off after 50 with a few flops like **Déjà Vu** (which I didn't mind) and **2 Guns**.
+Look I'm not calling him washed but...
+
 ## Results
 
+So we use this approach and plot out the median tomato index by age at production, giving us an idea of the *average performance above or below a career average* at each age.
+
 ```{r}
+
 # 
 rating_set =
-  films %>% 
-  select(title, year, tomatometer, director, actor_1:actor_3) %>%
-  gather("role", "name", director, actor_1:actor_3) %>%
-  inner_join(film_folk) %>%
-  filter(!is.na(gender)) %>%
-  mutate(
-    age_at_production = year - dob_year,
-    category = case_when(
-      role == "director" ~ "director",
-      gender == "male" ~ "male_actor",
-      TRUE ~ "female_actor"
-    )
+  master %>%
+  filter(
+    !(role %in% c("actor_4","actor_5", "actor_6")),
+    between(age_at_production, 15,85)
   ) %>%
-  filter(between(age_at_production, 15,85)) %>%
-  select(name, gender, age_at_production, category, tomatometer) %>%
   group_by(name) %>% 
   mutate(
-    average_tomato  = median(tomatometer),
+    average_tomato  = round(mean(tomatometer)),
     films = n()
-  ) %>% ungroup() %>%
+  ) %>% 
+  ungroup() %>%
+  mutate(tomato_index = (tomatometer - average_tomato) / average_tomato) %>%
   filter(films >= 5)
@@
   rating_set %>%
-  mutate(
-    tomato_index = tomatometer / average_tomato) %>%
   group_by(category, age_at_production) %>%
@@
   hc_yAxis(
-    title = list(text = "Probablity Density"),
-    min = 0.6
+    title = list(text = "Probablity Density")
   ) %>%
@@
 volume_chart
+```
+
+# The prime suspects
+
+```{r}
+
+actors = c("Robert De Niro", "Harvey Keitel", "Christopher Walken", "Bruce Willis", "Susan Sarandon", "Jeff Bridges", "Robin Williams", "Julianne Moore", "Steve Buscemi", "John Malkovich", "Meryl Streep", "Robert Redford")
+
+graphs = map(actors, function(actor) {
+
+  bucket = 5
+
+  actordata = 
+    master %>%
+    filter(
+      name == actor,
+      role %in% c("actor_1", "actor_2", "actor_3")
+    ) %>%
+    mutate(
+      average_tomato  = round(mean(tomatometer)),
+      tomato_index = (tomatometer - average_tomato) / average_tomato
+    ) %>%
+    mutate(age_bucket = round(age_at_production / bucket) * bucket) %>%
+    group_by(age_bucket) %>%
+    summarise(
+      index = mean(tomato_index),
+      films = n()) %>%
+    filter(films >= 3)
+
+  highchart() %>%
+    hc_add_theme(tmbish) %>%
+    hc_chart(
+      animation = list(duration = 2000)
+    ) %>%
+    hc_xAxis(
+      categories = actordata$age_bucket,
+      title = list(text = "Age at Production")
+    ) %>%
+    hc_title(text = actor) %>%
+    hc_add_series(
+      name = "Performance Index",
+      type = "spline",
+      data = actordata$index
+    ) %>%
+    hc_legend(enabled = FALSE)
+
+}) %>% hw_grid(ncol = 3, rowheight = 400) %>% browsable()
+
+graphs
+
 ```

### 2017-08-30 highcharts_theme.R

@@ -20,13 +20,13 @@ high_tmbish = function() {
       ),
       xAxis = list(
         lineWidth = 1, lineColor = "#011627",
-        gridLineWidth = 0.2, gridLineColor = "#011627", gridLineDashStyle = "LongDash",
+        gridLineWidth = 0.1, gridLineColor = "#011627", gridLineDashStyle = "LongDash",
         tickWidth = 0,
         title = list(style = header_style)
       ),
       yAxis = list(
         lineWidth = 1, lineColor = "#011627",
-        gridLineWidth = 0.2, gridLineColor = "#011627", gridLineDashStyle = "LongDash",
+        gridLineWidth = 0.1, gridLineColor = "#011627", gridLineDashStyle = "LongDash",
         minorGridLineWidth = 0.1, minorGridLineColor = "#011627",
         # tickColor = "#011627",tickLength = 10,
         # minorTickLength = 5, minorTickWidth = 1,
@@ -59,7 +59,8 @@ high_tmbish = function() {
       ),
       plotOptions = list(
         line = list(marker = list(symbol = "circle", lineWidth = 2, radius = 5)),
-        spline = list(marker = list(symbol = "circle", lineWidth = 2, radius = 5))
+        spline = list(marker = list(symbol = "circle", lineWidth = 2, radius = 5)),
+        column = list(dataLabels = list(backgroundColor = "#FFF"))
       ),
       legend = list(
         align = "right",

### 2017-08-31 01_actor_careers/05_report.Rmd
theme update!

@@
   summarise(rating = median(tomato_index)) %>%
+  filter(rating > -0.4) %>% # One outlier
   spread(category, rating)
@@
 # LOESS Trend Line
-loess_fit = loess(value ~ age_at_production , 
-                  data = rating_scores %>% gather("role", "value", -age_at_production)
-                  # %>% group_by(age_at_production) %>% summarise(value = mean(value, na.rm = TRUE))
-)
-
-predictions = loess_fit %>% predict(seq(15,85))
+predictions = loess(value ~ age_at_production , data = rating_scores %>% gather("role", "value", -age_at_production)) %>% predict(seq(15,85))
 
@@
   hc_add_theme(tmbish) %>%
-  hc_chart(height = "300") %>%
+  hc_chart(height = 300, spacingRight = 100) %>%
   hc_xAxis(categories = rating_volumes$age_at_production, opposite = TRUE) %>%
@@
     categories = rating_scores$age_at_production,
-    title = list(text = "Age at Production")
+    title = list(text = "Age at Production"),
+    plotBands = list(
+       list(
+         from = 27-15, 
+         to = 35-15,
+         color = "rgba(255,106,92,0.2)",
+         label = list(text = "Acting prime: 27-35!", style=list(fontFamily="Arvo",fontWeight="bold", fontSize=10), verticalAlign="middle"))
+    )
   ) %>%
   hc_yAxis(
-    title = list(text = "Probablity Density")
+    title = list(text = "Probablity Density"),
+    min = -0.4,
+    labels = list(
+      formatter = JS("function(){return(this.value*100 + '%')}")
+    )
   ) %>%
@@
     ) %>%
+    hc_yAxis(labels = list(formatter = JS("function(){return(this.value*100 + '%')}"))) %>%
     hc_title(text = actor) %>%

### 2017-08-31 highcharts_theme.R

@@ -11,7 +11,8 @@ high_tmbish = function() {
         backgroundColor = "#FDFFFC",
         style = list(
           fontFamily = base_font
-        )
+        ),
+        shadow = TRUE
       ),
       colors = list("#FF9F1C", "#2EC4B6", "#FE5F55", "#C1E1F1", "#5FEF9B"),
       title = list(

### 2017-08-31 01_actor_careers/05_report.Rmd
Many updates

@@
 
-> insert an image
+<br>
+
+![Nah but actually The Intern was ok.](deniro.jpg)
+
+<br>
 
@@
   hc_add_theme(tmbish) %>%
-  hc_chart(height = 300, spacingRight = 100) %>%
+  hc_chart(height = 300, spacingRight = 125) %>%
   hc_xAxis(categories = rating_volumes$age_at_production, opposite = TRUE) %>%
@@
 
+<style>
+
+.finding {
+  background-color:#FF6A5C;
+  height: 100px;
+  color: #FFF;
+  display: flex;
+  padding-top: 10px;
+  padding-bottom: 10px;
+  border-radius: 25px;
+  align-items: center;
+  text-align:center;
+
+}
+
+.finding .sidebar {
+  width: 20%;
+  font-weight: bold;
+  font-size: 14pt;
+}
+
+.finding .body {
+  width: 80%
+}
+
+.finding img {
+  display : block;
+  margin : auto;
+}
+
+</style>
+
+<br>
+
+<div class="finding">
+
+  <div class="sidebar"><img src="lightbulb.png"><span> Finding!</span></div>
+
+  <div class="body"> <span> So based on this 10 film sample Denzel had a solid 40s where his films (of the likes Hurricane and Courage Under Fire) average a rotten tomatoes rating about 20% above his career average </span> </div>
+
+</div>
+
+<br>
+
 # The prime suspects
@@
     hc_chart(
-      animation = list(duration = 2000)
+      animation = list(duration = 2000), shadow = FALSE
     ) %>%

### 2017-08-31 highcharts_theme.R

@@ -21,14 +21,14 @@ high_tmbish = function() {
       ),
       xAxis = list(
         lineWidth = 1, lineColor = "#011627",
-        gridLineWidth = 0.1, gridLineColor = "#011627", gridLineDashStyle = "LongDash",
+        gridLineWidth = 0.1, gridLineColor = "#414141", gridLineDashStyle = "LongDash",
         tickWidth = 0,
         title = list(style = header_style)
       ),
       yAxis = list(
         lineWidth = 1, lineColor = "#011627",
-        gridLineWidth = 0.1, gridLineColor = "#011627", gridLineDashStyle = "LongDash",
-        minorGridLineWidth = 0.1, minorGridLineColor = "#011627",
+        gridLineWidth = 0.1, gridLineColor = "#414141", gridLineDashStyle = "LongDash",
+        minorGridLineWidth = 0, minorGridLineColor = "#414141",
         # tickColor = "#011627",tickLength = 10,
         # minorTickLength = 5, minorTickWidth = 1,
         tickWidth = 0,

### 2017-09-01 01_actor_careers/04_analyse.R
Major reorg of folder

@@ -1,313 +1,0 @@
-library(readr)
-library(dplyr)
-library(highcharter)
-library(ggplot2)
-library(tidyr)
-library(gender)
-library(stringr)
-library(lubridate)
-
-# Data --------------------------------------------------------------------
-films = read_csv("https://raw.githubusercontent.com/TMBish/lab_posts/master/01_actor_careers/00_full_film_data.csv") %>%
-  filter(!is.na(title))
-
-
-film_folk=read_csv("https://raw.githubusercontent.com/TMBish/lab_posts/master/01_actor_careers/00_actors_directors.csv")
-film_folk[film_folk$dob < as.Date("1880-01-01"), "dob"] = as.Date("1880-01-01")
-
-# Grep out first name and dob year for the gender function
-film_folk = 
-  film_folk %>%
-  mutate(
-    first_name = str_extract(name, "(?i)[a-z]+(?=\\s)"),
-    dob_year = year(dob)
-  )
-  
-# Distinct name, dob combos and predict gender
-genders = 
-  film_folk %>% 
-  distinct(first_name, dob_year) %>%
-  gender_df(name_col = "first_name", year_col = "dob_year") %>%
-  select("first_name" = name, gender, "dob_year" = year_min)
-
-film_folk = 
-  film_folk %>%
-  left_join(genders)
-
-x = 19
-
- # The deal with directors? --------------------------------------------------------------------
-dir_data =
-  films %>% 
-  select("name" = director) %>%
-  inner_join(film_folk) %>%
-  group_by(gender) %>%
-  summarise(
-  	films = n()
-  ) %>%
-  filter(!is.na(gender))
-
-# Most are men Yep
-
- # Volumes By Age --------------------------------------------------------------------
-
-volume_data =
-  films %>% 
-  select(title, year, tomatometer, director, actor_1:actor_6) %>%
-  gather("role", "name", director, actor_1:actor_6) %>%
-  mutate(role = ifelse(role == "director", "Director", "Actor")) %>%
-  inner_join(film_folk) %>%
-  mutate(
-    age_at_production = year - dob_year
-  ) %>%
-  filter(between(age_at_production, 10,100)) %>%
-  select(name, gender, dob_year, age_at_production, year, role, tomatometer)
-
-
-	# Ggplot
-	var = "Director"
-	temp = 
-		volume_data %>%
-		filter(
-			role == var,
-			!is.na(gender)
-		)
-
-
-	ggplot(data = temp) +
[…]

### 2017-09-01 01_actor_careers/code.R

@@ -1,108 +1,0 @@
-
-get_tomatoes = function(actor) {
-  
-  require(rvest)
-  require(stringr)
-  require(dplyr)
-  
-  actor_string = str_replace_all(str_replace_all(tolower(actor), " ", "_"),"[\\-\\.]"," ")
-  
-  celeb_url = sprintf("https://www.rottentomatoes.com/celebrity/%s/", actor_string)
-  
-  
-  # Function to decode rotten tomatoes credit string into english
-  #   only interested in actor, director, or actor / director roles
-  assign_role = function(credit_string) {
-    
-    # Remove produce, screenwriter credits
-    credit_string = str_replace_all(credit_string, "(?i)producer|screenwriter|(executive producer)"  ,"")
-    
-    if (grepl("director", credit_string, ignore.case = TRUE)){
-      
-      aug = str_replace_all(credit_string, "(?i)director", "")
-      
-      if (grepl("(actor)|[a-z]{3,}", aug, ignore.case = TRUE)) {
-        
-        return("Actor / Director")
-        
-      } else {
-        
-        return("Director")
-        
-      }
-      
-    } else if (grepl("(actor)|[a-z]{3,}", credit_string, ignore.case = TRUE)) {
-      
-      return("Actor")
-      
-    } else {
-      
-      # Must be a producer or some shit
-      return("Null")
-      
-    }
-    
-  }
-  
-  # Scraping the filmography table using rvest
-  # got the Xpath / CSS id of the table
-  films = tryCatch(
-    {
-      
-      film_tables = tryCatch({
-        #Most URLS look like "Tom_Bishop"  
-        celeb_url %>%
-          read_html() %>%
-          html_nodes(xpath = "//*[@id='filmographyTbl']") %>%
-          html_table()        
-      }, error = function(e) {
-        #Some URLS randomly look like "Tom-Bishop"
-        person_string = str_replace_all(str_replace_all(tolower(person),"[\\-\\.]"," "), " ", "-")
-        celeb_url = sprintf("https://www.rottentomatoes.com/celebrity/%s/", person_string)        
-        return(
-          celeb_url %>%
-            read_html() %>%
-            html_nodes(xpath = "//*[@id='filmographyTbl']") %>%
-            html_table()
-        )  
-      })
-      
-      
-      films = film_tables[[1]]
-      
-      names(films) = tolower(names(films))
-      
-      films$role = lapply(films$credit, assign_role)
-      
[…]

### 2017-09-01 01_actor_careers/render_article.R

@@ -1,4 +1,0 @@
-library(knitr)
-
-
-rmarkdown::render("C:/Users/Tom Bishop/Desktop/lab_posts/01_actor_careers/05_report.Rmd")

### 2017-09-01 01_actor_careers/scraps.R

@@ -1,78 +1,0 @@
-
-library(tidyr)
-
-data =
-  films %>% 
-  select(title, year, tomatometer, director, actor_1:actor_3) %>%
-  gather("role", "name", director, actor_1:actor_3) %>%
-  mutate(role = ifelse(role == "director", "Director", "Actor")) %>%
-  inner_join(film_folk) %>%
-  mutate(
-    age_at_production = year - dob_year
-  ) %>%
-  filter(between(age_at_production, 10,100)) 
-
-write_csv(data, "C:/Users/Tom Bishop/Desktop/test.csv")
-
-
-chart_data = 
-  data %>%
-  mutate(age_at_production = as.character(age_at_production)) %>%
-  group_by(age_at_production) %>%
-  summarise(films = n())
-
-test = hchart(chart_data, "column", hcaes(x = age_at_production, y = films)) %>%
-  hc_add_theme(tmbish)
-
-
-chart_data = 
-  data %>%
-  mutate(age_at_production = as.character(age_at_production)) %>%
-  group_by(age_at_production, role) %>%
-  summarise(films = n()) %>%
-  spread(role, films)
-
-test = hchart(chart_data, "column", hcaes(x = age_at_production, y = films, group = role)) %>%
-  hc_add_theme(tmbish)
-
-actor = density(chart_data$Actor[!is.na(chart_data$Actor)])
-director = density(chart_data$Director[!is.na(chart_data$Director)])
-
-highchart() %>% 
-  hcdensity(actor) %>%
-  hc_add
-
-
-
-test = 
-  films %>%
-  inner_join(film_folk, by = c("director" =  "name")) %>%
-  mutate(
-    age_at_production = year - dob_year
-  ) %>%
-  filter(age_at_production > 20) %>%
-  mutate(age_bucket = )
-
-chart_data = 
-  test %>%
-  mutate(age_bucket = paste(round(age_at_production/10) *10, "-", round(age_at_production/10) *10 + 10)) %>%
-  select(tomatometer, age_bucket)
-  
-
-library(highcharter)
-test_chart = 
-  hchart(chart_data, "scatter", hcaes(x = age_at_production, y = tomatometer)) %>%
-  hc_theme(tmbish)
-
-test_chart = 
-  hcboxplot(x = chart_data$tomatometer, var = chart_data$age_bucket) %>%
-  hc_add_theme(tmbish)
-
-highchart() %>%
[…]

### 2017-09-01 01_halflife-of-acting-talent/web-scrape/01_get-bio.R

@@ -1,3 +1,4 @@
+# Function takes an actor's name and returns their filmography from Rotten Tomatoes
 get_bio = function(person) {
   
   require(rvest)

### 2017-09-01 01_halflife-of-acting-talent/web-scrape/02_parse-film.R

@@ -1,3 +1,5 @@
+
+# Function takes the Rotten Tomatoes URL exension of a film and returns a list with key information / stats about the film
 parse_film = function(url_extension) {
   
   require(rvest)

### 2017-09-01 01_halflife-of-acting-talent/web-scrape/03_scrape-loop.R

@@ -73,37 +73,37 @@ for (row in 1:nrow(film_folk)) {
   film_folk[row,"dob"] = details$dob
 
   # Get URLS
-  # urls = details$url %>% distinct(url_extension)
+  urls = details$url %>% distinct(url_extension)
   
-  # # DRY = DON'T REPEAT YOURSELF
-  # if ( nrow(films) > 0) {
-  #   # Remove movies we've already scraped
-  #   starting_rows = nrow(urls)
-  #   urls = 
-  #     urls %>%
-  #     anti_join(films %>% select(url), by = c("url_extension" = "url"))
+  # DRY = DON'T REPEAT YOURSELF
+  if ( nrow(films) > 0) {
+    # Remove movies we've already scraped
+    starting_rows = nrow(urls)
+    urls = 
+      urls %>%
+      anti_join(films %>% select(url), by = c("url_extension" = "url"))
     
-  #   if(starting_rows != nrow(urls)) {
-  #     cat(glue("Already recorded {starting_rows - nrow(urls)} films!"), "\n")
-  #   }
+    if(starting_rows != nrow(urls)) {
+      cat(glue("Already recorded {starting_rows - nrow(urls)} films!"), "\n")
+    }
     
-  #   if (nrow(urls)== 0) {next}
-  # }
+    if (nrow(urls)== 0) {next}
+  }
 
-  # # Initialise the cluster
-  # film_list = as.list(urls$url_extension)
-  # no_cores = max(detectCores() - 2,1)
-  # cl = makeCluster(no_cores)
+  # Initialise the cluster
+  film_list = as.list(urls$url_extension)
+  no_cores = max(detectCores() - 2,1)
+  cl = makeCluster(no_cores)
   
-  # # Multithread the film detail extraction
-  # results = parLapply(cl, film_list, parse_film)
+  # Multithread the film detail extraction
+  results = parLapply(cl, film_list, parse_film)
 
-  # # Close the cluster
-  # stopCluster(cl)
+  # Close the cluster
+  stopCluster(cl)
  
-  # to_df = do.call(rbind.data.frame, results)
+  to_df = do.call(rbind.data.frame, results)
   
-  # films = rbind(films, to_df)
+  films = rbind(films, to_df)
   
 }
 

### 2017-09-01 01_halflife-of-acting-talent/article.Rmd
func

--- 2017-08-31 01_actor_careers/05_report.Rmd
@@
 library(htmltools)
+library(pander)
 
@@
 # Highcharts theme
-source("https://raw.githubusercontent.com/TMBish/lab_posts/master/highcharts_theme.R")
+source("https://raw.githubusercontent.com/TMBish/lab_posts/master/00_utilities/highcharts-theme.R")
 tmbish = high_tmbish()
+
+# Finding function
+
+create_finding = function(finding_text) {
+
+  html = glue::glue("
+
+  <style>
+
+  .finding {
+    background-color:#FF6A5C;
+    height: 100px;
+    color: #FFF;
+    display: flex;
+    padding-top: 10px;
+    padding-bottom: 10px;
+    border-radius: 25px;
+    align-items: center;
+    text-align:center;
+  }
+
+  .finding .sidebar { 
+    width: 20%;
+    font-weight: bold;
+    font-size: 14pt;
+  }
+
+  .finding .body {
+    width: 80%
+  }
+
+  .finding img {
+    display : block;
+    margin : auto;
+  }
+
+  </style>
+
+    <br>
+
+    <div class='finding'>
+
+      <div class='sidebar'><img src='https://github.com/TMBish/lab_posts/blob/master/00_utilities/lightbulb.png?raw=true'><span> Finding!</span></div>
+
+      <div class='body'> <span> <<finding_text>> </span> </div>
+
+    </div>
+
+    <br>" %>% str_replace_all("\\n", ""), .open = "<<", .close = ">>")
+
+  return(html)
+
+}
+
 ```
@@
 
-Variable | Description
------------- | ---------------------
-url | URL extension on rotten tomatoes website
-year | Film production year
-title | Film title
-reviews | Count of formal critic reviews of film
-tomatometer | Percentage of favourable reviews
-av_rating | Average rating of film out of 10
-audience | The non-critic plebian equivolent of the tomatometer
-box_office | The box-office revenue
-director | The film's director
-actor_1:actor_6 | The 6 top actors according to rotten tomatoes internal ranking (seemingly ordered by screen time)
+```{r results='asis'}
+
+dict = data.frame(
+  Variable = c("url", "year", "title", "reviews", "tomatometer", "av_rating", "audience", "box_office", "director", "actor_1:actor_6"),
+  Description = c("URL extension on rotten tomatoes website", "Film production year", "Film title", "Count of formal critic reviews of film", "Percentage of favourable reviews", "Average rating of film out of 10", "The non-critic plebian equivolent of the tomatometer", "The box-office revenue", "The film's director", "The 6 top actors according to rotten tomatoes internal ranking (seemingly ordered by screen time)")
+)
+
+dict %>% pandoc.table()
+
+```
 
@@
 Let's have a look at the films data set
-```{r}
+```{r results='asis'}
 # Load in films data from Github Repo
-films = read_csv("https://raw.githubusercontent.com/TMBish/lab_posts/master/01_actor_careers/00_full_film_data.csv") %>% filter(!is.na(title))
+films = read_csv("https://raw.githubusercontent.com/TMBish/lab_posts/master/01_halflife-of-acting-talent/data/film-data.csv") %>% filter(!is.na(title))
 
 films %>% 
-  select(-url) %>%
-  sample_n(5) %>%
-  knitr::kable()
+  filter(title %in% c("The Departed", "Titanic", "No Country for Old Men", "Snatch.", "Superbad")) %>%
+  pandoc.table(emphasize.strong.cols = 3, missing="?")
 
@@
 
-film_folk = read_csv("https://raw.githubusercontent.com/TMBish/lab_posts/master/01_actor_careers/00_actors_directors.csv")
+film_folk = read_csv("https://raw.githubusercontent.com/TMBish/lab_posts/master/01_halflife-of-acting-talent/data/actors-directors.csv")
 
@@
 
-```{r}
+```{r results='asis'}
 genders %>%
   sample_n(10) %>%
-  knitr::kable()
+  select(first_name, dob_year, gender) %>%
+  pandoc.table(emphasize.strong.cols = 3)
 ```
@@
 Finally we'll need to join this information back to the individual data set.
-
-```{r}
-# Join back the gender back to the main data
-film_folk = 
-  film_folk %>%
-  left_join(genders)
-
-```
 
@@
 ```{r}
+# Join back the gender back to the main data
+film_folk = 
+  film_folk %>%
+  left_join(genders)
+
 # Establish a persistent dataset of interest
@@
 
+gender_prop_finding = create_finding("The average age of a female actor at the time of film production is 28!")
+
 gender_props %>%
@@
 
-> Insert finding graphic thing
+```{r results='asis'}
+
+gender_prop_finding
+
+```
 
@@
 
-> Hypothesis 2: acting and directing skills aren't tied to a person's physical attributes so shouldn't experience deterioration in age.
-In fact you would expect these artists to improve their skills with age.
-
-## Measuring Performance
-
 To investigate this hypothesis we must make a couple of assumptions.
@@
 
-```{r echo=FALSE}
+```{r echo=FALSE, results='asis'}
 master %>% 
@@
   mutate(tomato_index = scales::percent(tomato_index)) %>%
-  knitr::kable()
+  pandoc.table(emphasize.strong.cols = 7)
 
@@
 
-<style>
-
-.finding {
-  background-color:#FF6A5C;
-  height: 100px;
-  color: #FFF;
-  display: flex;
-  padding-top: 10px;
-  padding-bottom: 10px;
-  border-radius: 25px;
-  align-items: center;
-  text-align:center;
-
-}
-
-.finding .sidebar {
-  width: 20%;
-  font-weight: bold;
-  font-size: 14pt;
-}
-
-.finding .body {
-  width: 80%
-}
-
-.finding img {
-  display : block;
-  margin : auto;
-}
-
-</style>
-
-<br>
-
-<div class="finding">
-
-  <div class="sidebar"><img src="lightbulb.png"><span> Finding!</span></div>
-
-  <div class="body"> <span> So based on this 10 film sample Denzel had a solid 40s where his films (of the likes Hurricane and Courage Under Fire) average a rotten tomatoes rating about 20% above his career average </span> </div>
-
-</div>
-
-<br>
-
 # The prime suspects

### 2017-09-02 01_halflife-of-acting-talent/article.Rmd
formatting changes

@@
 <br>
+
+<style>
+
+.finding {
+  background-color:#000;
+  height: 125px;
+  color: #FFF;
+  display: flex;
+  border-radius: 25px;
+  align-items: center;
+  text-align:center;
+}
+
+.finding .sidebar { 
+  padding-top:15px;
+  width: 30%;
+  font-weight: bold;
+  font-size: 18px;
+}
+
+.finding .body {
+  width: 70%;
+  text-align:left;
+  font-size: 16px;
+  padding-right:10px
+}
+
+.finding .body p {
+  margin-bottom:0;
+}
+
+.finding img {
+  display : block;
+  margin : auto;
+}
+
+#the-half-list-of-acting-talent img {
+  height: 200px; 
+  display:block; 
+  margin: 0 auto;
+}
+
+</style>
 
@@
 
-  html = glue::glue("
+  html = 
+glue::glue("<br><br><div class='finding'>
 
-  <style>
-
-  .finding {
-    background-color:#FF6A5C;
-    height: 100px;
-    color: #FFF;
-    display: flex;
-    padding-top: 10px;
-    padding-bottom: 10px;
-    border-radius: 25px;
-    align-items: center;
-    text-align:center;
-  }
-
-  .finding .sidebar { 
-    width: 20%;
-    font-weight: bold;
-    font-size: 14pt;
-  }
-
-  .finding .body {
-    width: 80%
-  }
-
-  .finding img {
-    display : block;
-    margin : auto;
-  }
-
-  </style>
-
-    <br>
-
-    <div class='finding'>
-
-      <div class='sidebar'><img src='https://github.com/TMBish/lab_posts/blob/master/00_utilities/lightbulb.png?raw=true'><span> Finding!</span></div>
-
-      <div class='body'> <span> <<finding_text>> </span> </div>
-
+<div class='sidebar'>
+  <img src='https://github.com/TMBish/lab_posts/blob/master/00_utilities/lightbulb.png?raw=true'>
+  <span> Finding!</span>
 </div>
 
-    <br>" %>% str_replace_all("\\n", ""), .open = "<<", .close = ">>")
+<div class='body'> 
+  <span> {finding_text} </span> 
+</div>
+
+</div><br><br>")
 
@@
 
-dict %>% pandoc.table()
+dict %>% pandoc.table(style = "rmarkdown")
 
@@
   filter(title %in% c("The Departed", "Titanic", "No Country for Old Men", "Snatch.", "Superbad")) %>%
-  pandoc.table(emphasize.strong.cols = 3, missing="?")
+  pandoc.table(emphasize.strong.cols = 3, missing="?", style = "rmarkdown", justify="left",split.cells=15)
 
@@
   select(first_name, dob_year, gender) %>%
-  pandoc.table(emphasize.strong.cols = 3)
+  pandoc.table(emphasize.strong.cols = 3, style = "rmarkdown", justify="left", split.cells=15)
 ```
@@
 Things get dicey with unisex names like Sandy; however, the package must know that most Sandys born in 1937 were female so we'll have to trust it here.
-Finally we'll need to join this information back to the individual data set.
 
@@
 
-gender_prop_finding = create_finding("The average age of a female actor at the time of film production is 28!")
+gender_prop_finding = create_finding("Approximately 80% of all directors are male, and 85% of popular films are directed by a man.")
 
@@
 
-So henceforth we'll treat directors as a single bloc and you can assume that they're male statistically speaking.
+So we'll treat directors as a single group that, statistically speaking, are very much likely to be males.
 
-# I starred in or directed a film; how old am I likely to be?
+# What's a typical career length?
 
-Well, as it turns out, it depends.
-We'll group individuals in groups: directors (predominantly male as seen above), male actors, and female actors.
-For all these individuals we calculate their age at the time a film they were in was realeased and plot the densities within each group.
+Well, as it turns out, it depends on which one of the above groups you're in.
+To remind you, our groups are: directors (predominantly male as seen above), male actors, and female actors.
+For all these individuals we calculate their age at the time they were involved in a realeased film and plot the distribution within each group.
 
-Switch between the denisty (proportion appearing at one speicific age) and cumulative distribution (proportion appearing at **or before** at specific age) views to better understand the data.
+Click on the male and director series to compare with the female one shown below.
+Additionally, switch between the denisty view (proportion appearing at one speicific age) and cumulative distribution view (proportion appearing at **or before** at specific age) to better understand the data.
 
@@
 
+age_atprod_finding = create_finding("64% of female roles are given to actors under the age of 40 compared with 42% of male roles. Only 28% of popular films are directed by a someone under 40.")
+
 age_dist_chart
@@
 
-> Insert infographic thing
-
 # The half life of acting talent
 
+Our ultimate question is: do actors and directors improve or deteriorate as they get older.
 To investigate this hypothesis we must make a couple of assumptions.
-Since we don't have individual actor / director performance metrics (like we have in sports) we'll have to assume an actor or director can have a material affect on the quality of the movie they appear in; there are obviously many other factors but this seems like a relatively safe assumption.
+Since we don't have individual actor or director performance metrics (like we have in sports) we'll have to assume an actor or director can have a material affect on the quality of the moviesthey appear in.
+There are obviously many other factors that go into the quality of a film but this seems like a relatively safe assumption.
 
@@
 
-<iframe width="560" height="315" src="https://www.youtube.com/embed/qIKPJlKHKxg" frameborder="0" allowfullscreen></iframe>
+<br>
+
+<iframe width="560" height="315" style="display:block;margin: 0 auto;" src="https://www.youtube.com/embed/qIKPJlKHKxg" frameborder="0" allowfullscreen></iframe>
+
+<br>
 
@@
 
-> INSERT EXAMPLES FROM A FEW ROTTEN TOMATOES PAGES
+### Snatch
 
-## Methodology
+![](snatch.png)
+
+### No Country For Old Men
+
+![](no-country-for-old-men.png)
+
+### The Departed
+
+![](the-departed.png)
+
+So we'll limit this dataset to the top 3 actors in each film.
 
 There's a few other things we want to control for here.
-I don't want to plot raw film critical rating because we might be prone to idiosyncracies of groups or ages - high performing directors might generally wait until they feel experienced enough to direct their first film as an example.
+I don't necessarily want to plot raw film critical rating because this might be prone to idiosyncracies within groups or ages - for example, high performing directors might generally wait until they feel experienced enough to direct their first film.
 
-Instead we'll plot, for each individual and film, how well they have perfomed relative to that individual's mean lifetime score (the average tomatometer of all that individual's films).
-This gives us a common scale on which to compare.
-
-To illustrate this approach let's look at Denzel Washington's films. Denzel has a healthy mean tomatometer of 68%.
+Instead we'll plot, for each individual and film, how well they have perfomed relative to that individual's career average (the average tomatometer of all that individual's films).
+To illustrate this approach let's look at Denzel Washington's films.
+Denzel has a healthy mean tomatometer of 68%.
 
 ```{r echo=FALSE, results='asis'}
+
 master %>% 
@@
   arrange(age_at_production) %>%
-  select(title, name, year, age_at_production, tomatometer, average_tomato, tomato_index) %>%
+  select(title, year, age_at_production, tomatometer, average_tomato, tomato_index) %>%
   mutate(tomato_index = scales::percent(tomato_index)) %>%
-  pandoc.table(emphasize.strong.cols = 7)
+  pandoc.table(emphasize.strong.cols = 6, style = "rmarkdown", justify="left")
 
@@
 
-So based on this 10 film sample Denzel had a solid 40s where his films (of the likes **Hurricane** and **Courage Under Fire**) average a rotten tomatoes rating about 20% above his career average.
+So based on this 10 film sample Denzel had a solid early 40s where his films (of the likes **Hurricane** and **Courage Under Fire**) average a rotten tomatoes rating about 20% above his career average.
 He looks like he dropped off after 50 with a few flops like **Déjà Vu** (which I didn't mind) and **2 Guns**.
-Look I'm not calling him washed but...
+Look I'm not calling him washed but he hasn't done anything good for a while.
 
-## Results
+## Prime Suspects
 
-So we use this approach and plot out the median tomato index by age at production, giving us an idea of the *average performance above or below a career average* at each age.
+To help visualise this approach let's take 12 of the top 20 actors by volume and visualise average their film rating performance by age.
+De Niro is a great example of someone who starred in increasingly poor films as he got older - clearly visible in the chart below..
+Obviously this probably has more to do with role selection than deteriorating skills (we'll discuss this later) but it's interesting to visualise nonetheless.
+
+```{r}
+
+actors = c("Robert De Niro", "Harvey Keitel", "Christopher Walken", "Bruce Willis", "Susan Sarandon", "Jeff Bridges", "Robin Williams", "Julianne Moore", "Denzel Washington", "John Malkovich", "Meryl Streep", "Robert Redford")
+
+graphs = map(actors, function(actor) {
+
+  bucket = 5
+
+  actordata = 
+    master %>%
+    filter(
+      name == actor,
+      role %in% c("actor_1", "actor_2", "actor_3")
+    ) %>%
+    mutate(
+      average_tomato  = round(mean(tomatometer)),
+      tomato_index = (tomatometer - average_tomato) / average_tomato
+    ) %>%
+    mutate(age_bucket = round(age_at_production / bucket) * bucket) %>%
+    group_by(age_bucket) %>%
+    summarise(
+      index = mean(tomato_index),
+      films = n()) %>%
+    filter(films >= 3)
+
+  highchart() %>%
+    hc_add_theme(tmbish) %>%
+    hc_chart(
+      animation = list(duration = 2000), shadow = FALSE
+    ) %>%
+    hc_xAxis(
+      categories = actordata$age_bucket,
+      title = list(text = "Age at Production")
+    ) %>%
+    hc_yAxis(labels = list(formatter = JS("function(){return(this.value*100 + '%')}"))) %>%
+    hc_title(text = actor) %>%
+    hc_add_series(
+      name = "Performance Index",
+      type = "spline",
+      data = actordata$index
+    ) %>%
+    hc_legend(enabled = FALSE)
+
+}) %>% hw_grid(ncol = 3, rowheight = 350) %>% browsable()
+
+graphs
+
+```
+
+## The holistic trend
+
+So let's extend this approach and plot out the median tomato index by age at production, giving us an idea of the *average performance above or below a career average* at each age.
 
@@
 
-# The prime suspects
+```{r results='asis'}
 
-```{r}
+actor_prime_finding = create_finding("Actors and Directors work in their most critically acclaimed films - about 10% above their career average - between 27 and 35 years old.")
 
-actors = c("Robert De Niro", "Harvey Keitel", "Christopher Walken", "Bruce Willis", "Susan Sarandon", "Jeff Bridges", "Robin Williams", "Julianne Moore", "Steve Buscemi", "John Malkovich", "Meryl Streep", "Robert Redford")
-
-graphs = map(actors, function(actor) {
-
-  bucket = 5
-
-  actordata = 
-    master %>%
-    filter(
-      name == actor,
-      role %in% c("actor_1", "actor_2", "actor_3")
-    ) %>%
-    mutate(
-      average_tomato  = round(mean(tomatometer)),
-      tomato_index = (tomatometer - average_tomato) / average_tomato
-    ) %>%
-    mutate(age_bucket = round(age_at_production / bucket) * bucket) %>%
-    group_by(age_bucket) %>%
-    summarise(
-      index = mean(tomato_index),
-      films = n()) %>%
-    filter(films >= 3)
-
-  highchart() %>%
-    hc_add_theme(tmbish) %>%
-    hc_chart(
-      animation = list(duration = 2000), shadow = FALSE
-    ) %>%
-    hc_xAxis(
-      categories = actordata$age_bucket,
-      title = list(text = "Age at Production")
-    ) %>%
-    hc_yAxis(labels = list(formatter = JS("function(){return(this.value*100 + '%')}"))) %>%
-    hc_title(text = actor) %>%
-    hc_add_series(
-      name = "Performance Index",
-      type = "spline",
-      data = actordata$index
-    ) %>%
-    hc_legend(enabled = FALSE)
-
-}) %>% hw_grid(ncol = 3, rowheight = 400) %>% browsable()
-
-graphs
+actor_prime_finding
 
 ```
+
+# Caveats & Conclusions
+
+While blah blah blah
 

### 2017-09-03 01_halflife-of-acting-talent/article.Rmd
Datatables tables

@@
 
-There are significant confounding factors that might prevent us from answering this question difinitively (which I'll discuss later) but let's dig into the data.
+There are some confounding factors that might prevent us from answering this question difinitively (which I'll discuss later) but let's dig into the data.
 
@@
 library(pander)
+library(DT)
 
@@
 
-dict %>% pandoc.table(style = "rmarkdown")
+dict %>% pandoc.table(justify='left')
 
@@
 
-Let's have a look at the films data set
+Let's have a look at the films data set. Click the blue `+` button to view the extra fields in the dataset (the director and top 6 actors in the film).
+
+<br>
 ```{r results='asis'}
@@
   filter(title %in% c("The Departed", "Titanic", "No Country for Old Men", "Snatch.", "Superbad")) %>%
-  pandoc.table(emphasize.strong.cols = 3, missing="?", style = "rmarkdown", justify="left",split.cells=15)
+  datatable(
+    style = 'bootstrap',
+    class = 'table-hover',
+    rownames=FALSE,
+    autoHideNavigation = TRUE,
+    extensions = 'Responsive'
+
+  )
 
 ```
+<br>
 
@@
 The `gender` R package allows you to infer a person's gender from their first name and DOB.
-The result is a probabilistic estimate of that individuals most likely gender given their first name and DOB.
+The result is a probabilistic estimate of that individuals most likely gender given their first name and the year they were born.
 
@@
 
-We should sense check the gender mapping to make sure the package is making logical inferences. Let's take a random 10 person sample:
+Pretty cool, but we should sense check the gender mapping to make sure the package is making logical guesses. Let's take a random 10 person sample:
+
+<br>
 
@@
   select(first_name, dob_year, gender) %>%
-  pandoc.table(emphasize.strong.cols = 3, style = "rmarkdown", justify="left", split.cells=15)
+  datatable(
+  style = 'bootstrap',
+  class = 'table-hover',
+  rownames=FALSE,
+  autoHideNavigation = TRUE
+  )
 ```
+
+<bt>
 
@@
 To remind you, our groups are: directors (predominantly male as seen above), male actors, and female actors.
-For all these individuals we calculate their age at the time they were involved in a realeased film and plot the distribution within each group.
+For all these individuals we calculate their age at the time they were credited in a film release and plot the distribution within each group.
 
@@
     type = "spline",
+    visible= FALSE,
     data = chart_data$director,
@@
     type = "spline",
+    visible= FALSE,
     data = chart_data$male_actor,
@@
     data = chart_data$female_actor,
-    zIndex = -10
-    #marker = list(enabled = FALSE)
-    #fillOpacity = 0.5
+    zIndex = -10,
+    marker = list(enabled = FALSE)
+  ) %>%
+  hc_tooltip(
+    formatter = JS("function(){return('<b> Series: </b>' + point.key + '<br> <b> Age: </b>' + this.x + '<b> Value: </b>' + this.y )}")
   )
@@
 To investigate this hypothesis we must make a couple of assumptions.
-Since we don't have individual actor or director performance metrics (like we have in sports) we'll have to assume an actor or director can have a material affect on the quality of the moviesthey appear in.
+Since we don't have individual actor or director performance metrics (like we have in sports) we'll have to assume an actor or director can have a material affect on the quality of the movies they appear in.
 There are obviously many other factors that go into the quality of a film but this seems like a relatively safe assumption.
@@
 Further - for actors - we'll have to limit the dataset to actors that played an important role in the film.
-To implement an `actor performance == film quality` approach the actors need to be noteworthy enough to be able to affect the overall quality of the film.
-So while Michael Cera's cameo in **This is the End** was high quality it can't be said that he influenced the rotten tomatoes rating of the film on his own.
+To implement an `actor performance == film quality` approach the actors need to be influential enough to be able to affect the overall quality of the film.
+So while Michael Cera's cameo in **This is the End** was high quality, it can't be said that he influenced the rotten tomatoes rating of the film on his own.
 
@@
 There's a few other things we want to control for here.
-I don't necessarily want to plot raw film critical rating because this might be prone to idiosyncracies within groups or ages - for example, high performing directors might generally wait until they feel experienced enough to direct their first film.
+I don't necessarily want to plot raw film critical rating because this might be prone to idiosyncracies within groups or ages - for example, high performing directors might generally wait until they are experienced enough to direct their first film.
 
-Instead we'll plot, for each individual and film, how well they have perfomed relative to that individual's career average (the average tomatometer of all that individual's films).
+Instead we'll plot, for each individual and film, how well they have perfomed relative to their career average (the average tomatometer of all that individual's films).
 To illustrate this approach let's look at Denzel Washington's films.
@@
 
+<br>
 ```{r echo=FALSE, results='asis'}
@@
   mutate(tomato_index = scales::percent(tomato_index)) %>%
-  pandoc.table(emphasize.strong.cols = 6, style = "rmarkdown", justify="left")
+  datatable(
+    style = 'bootstrap',
+    class = 'table-hover',
+    rownames=FALSE,
+    autoHideNavigation = TRUE,
+    extensions = 'FixedColumns',
+    options = list(
+      scrollX = TRUE,
+      fixedColumns = list(leftColumns = 1, rightColumns=1)
+    )
+  )
 
 ```
+<br>
 
-So based on this 10 film sample Denzel had a solid early 40s where his films (of the likes **Hurricane** and **Courage Under Fire**) average a rotten tomatoes rating about 20% above his career average.
+So based on this 10 film sample Denzel had a solid early 40s where his films (**Hurricane** and **Courage Under Fire** etc) averaged a rotten tomatoes rating about 20% above his career average.
 He looks like he dropped off after 50 with a few flops like **Déjà Vu** (which I didn't mind) and **2 Guns**.
@@
 To help visualise this approach let's take 12 of the top 20 actors by volume and visualise average their film rating performance by age.
-De Niro is a great example of someone who starred in increasingly poor films as he got older - clearly visible in the chart below..
-Obviously this probably has more to do with role selection than deteriorating skills (we'll discuss this later) but it's interesting to visualise nonetheless.
+De Niro is a great example of someone who starred in increasingly poor films as he got older - clearly visible in the chart below.
+This probably has more to do with role selection than deteriorating skills (we'll discuss this later) but it's interesting to visualise nonetheless.
 
@@
 
-## The holistic trend
+## The Upshot
 
@@
 
-While blah blah blah
+While it appears that actors and directors have their prime between the ages of 27-35 I don't think it's fair to say this is **caused** by a natural skill trajectory.
+Some caveats that could potentially explain this trend without our skills and abilities narrative:
+
+* Most films typically have non-elderly main characters; limiting the ability for an older, but still skillful, actor to be cast in these roles
+* Seperating an Actor's role **choice** vs their **performance** given they chose a particular role highlights the problem we see with De Niro above.
+It's quite possible that after career success and achievements actor's and directors prioritise different things (eg.
+*$Cash Money$*) in the twiglights of their careers.
+
+All we can say for sure is that the prime of your acting life (the quality of the films you're in) happens between 27-35.
+Whether that's becuase you were at the peak of your abilities, or you were more likely to be seeking critically acclaimed roles (hunting that first Oscar), or you were just given opportunities you wouldn't be afforded later in life we'll have to leave to another day.
 

### 2017-09-03 00_utilities/highcharts-theme.R

@@ -39,7 +39,6 @@ high_tmbish = function() {
         align = "left"
       ),
       tooltip = list(
-        borderWidth = 0,
         shape = "square",
         valueDecimals = 2,
         backgroundColor = "#FFF",

### 2017-09-04 01_halflife-of-acting-talent/article.Rmd
stuff

@@
 .finding {
-  background-color:#000;
+  background-color:#414141;
   height: 125px;
@@
   display: flex;
-  border-radius: 25px;
   align-items: center;
@@
   padding-top:15px;
-  width: 30%;
+  width: 20%;
   font-weight: bold;
@@
 .finding .body {
-  width: 70%;
+  width: 75%;
   text-align:left;
@@
 
-#the-half-list-of-acting-talent img {
+#snatch img {
+  height: 200px; 
+  display:block; 
+  margin: 0 auto;
+}
+
+#no-country-for-old-men img {
+  height: 200px; 
+  display:block; 
+  margin: 0 auto;
+}
+
+#the-departed img {
   height: 200px; 
@@
 # Finding function
-
-create_finding = function(finding_text) {
-
-  html = 
-glue::glue("<br><br><div class='finding'>
-
-<div class='sidebar'>
-  <img src='https://github.com/TMBish/lab_posts/blob/master/00_utilities/lightbulb.png?raw=true'>
-  <span> Finding!</span>
-</div>
-
-<div class='body'> 
-  <span> {finding_text} </span> 
-</div>
-
-</div><br><br>")
-
-  return(html)
-
-}
-
+source("https://raw.githubusercontent.com/TMBish/lab_posts/master/00_utilities/create-finding-html.R")
 ```
@@
 So generally this is looking pretty, pretty good.
-Things get dicey with unisex names like Sandy; however, the package must know that most Sandys born in 1937 were female so we'll have to trust it here.
+Things get dicey with unisex names like Sandy; however, the package must know that Sandy was more commonly used for females in the 1930s, which is consistent with my [1 data other point.](https://www.youtube.com/watch?v=cxbMk-8701M)
 
@@
       highchart() %>%
-      hc_chart(type = "column") %>%
+      hc_chart(type = "column", shadow=FALSE) %>%
       hc_add_theme(tmbish) %>%
       hc_xAxis(categories = data$role_type) %>%
+      hc_yAxis(title = list(text = ifelse(metric=="films", "Percentage of Total Roles", "Percentage of Distinct Individuals"))) %>%
       hc_plotOptions(
@@
             color = "#FFF",
+            backgroundColor = NULL,
             style = list(textOutline = NULL, fontSize = "14px"),
@@
       ) %>%
-      hc_title(text = ifelse(metric=="films", "By Volume of Films", "By Distinct Individuals")) %>%
-      hc_legend(align = "center", verticalAlign = "bottom", layout = "horizontal")
+      hc_title(text = ifelse(metric=="films", "By Volume of Roles", "By Distinct Individuals")) %>%
+      hc_legend(enabled=FALSE) %>%
+      hc_tooltip(
+        formatter = JS("function(){return('<b>Gender: </b>' + this.series.name + '<br> <b>Proportion: </b>' + Math.round(this.percentage) + '%')}")
+      )
+      # hc_legend(align = "center", verticalAlign = "bottom", layout = "horizontal")
 
@@
 
-    if (metric != "films") { base_chart  = base_chart %>% hc_legend(enabled=FALSE)}
-
   gender_props[[metric]] = base_chart
@@
 
-gender_prop_finding = create_finding("Approximately 80% of all directors are male, and 85% of popular films are directed by a man.")
+gender_prop_finding = create_finding("Approximately 85% of all directors are male, and almost 90% of popular films are directed by a man.")
 
 gender_props %>%
-  hw_grid(ncol = 1, rowheight = "400px") %>%
+  hw_grid(ncol = 2, rowheight = "400px") %>%
   browsable()
@@
 
-So we'll treat directors as a single group that, statistically speaking, are very much likely to be males.
+So we'll treat directors as a single group that, statistically speaking, are very likely to be male.
 
@@
   hc_title(text = "Age at Production") %>%
-  hc_subtitle(text = "Comparing the distribution of film professionals for age at the time of film productions") %>%
+  hc_subtitle(text = "Contrasting the distribution of ages at production across gender and role") %>%
   hc_add_series(
@@
   hc_tooltip(
-    formatter = JS("function(){return('<b> Series: </b>' + point.key + '<br> <b> Age: </b>' + this.x + '<b> Value: </b>' + this.y )}")
+        formatter = JS("function(){return('<b> Series: </b>' + this.series.name + '<br> <b>Age: </b>' + this.x + '<br> <b>Value: </b>' + Math.round(this.y*1000) / 10 +'%' )}")
   )
-
-age_atprod_finding = create_finding("64% of female roles are given to actors under the age of 40 compared with 42% of male roles. Only 28% of popular films are directed by a someone under 40.")
 
@@
 <button class="button secondary outline" id = "update_age_series"> Show Cumulative Distribution </button>
+
+```{r results='asis'}
+age_atprod_finding = create_finding("64% of female roles are given to actors under the age of 40 compared with 42% of male roles. Only 28% of popular films are directed by a someone under 40.")
+
+age_atprod_finding
+
+```
 
@@
     ) %>%
-    hc_legend(enabled = FALSE)
+    hc_legend(enabled = FALSE) %>%
+    hc_tooltip(
+         formatter = JS("function(){return('<b>Tomato Index: </b>' + Math.round(this.y*1000) / 10 +'%' )}")
+    )
 
-}) %>% hw_grid(ncol = 3, rowheight = 350) %>% browsable()
+}) %>% hw_grid(ncol = 3, rowheight = 250) %>% browsable()
 
@@
   hc_add_theme(tmbish) %>%
-  hc_chart(height = 300, spacingRight = 125) %>%
+  hc_chart(height = 300, spacingRight = 125, shadow=FALSE) %>%
   hc_xAxis(categories = rating_volumes$age_at_production, opposite = TRUE) %>%
@@
     type = "area",
+    fillOpacity = 0.25,
     data = rating_volumes$films,
@@
   ) %>% 
-  hc_legend(enabled = FALSE)
+  hc_legend(enabled = FALSE) %>%
+    hc_tooltip(
+       formatter = JS("function(){return('<b>Total Performances At This Age: </b>' + -1*this.y)}")
+  )
 
@@
   hc_chart(
-    animation = list(duration = 2000)
+    animation = list(duration = 2000),
+    shadow = FALSE
   ) %>%
@@
   ) %>%
-  hc_title(text = "Female actors") %>%
+  hc_title(text = "The Prime of Your Life") %>%
   hc_subtitle(text = "Comparing male actors, (male) directors and female actors") %>%
@@
     marker = list(enabled = FALSE)
+  ) %>%
+  hc_tooltip(
+        formatter = JS("function(){return('<b>Role Type: </b>' + this.series.name + '<br> <b>Age: </b>' + this.x + '<br> <b>Average Tomato Index: </b>' + Math.round(this.y*1000) / 10 +'%' )}")
   )
@@
 
-While it appears that actors and directors have their prime between the ages of 27-35 I don't think it's fair to say this is **caused** by a natural skill trajectory.
+While it appears that actors and directors have their prime between the ages of 27-35 we can't say with confidence that this is **caused** by a natural skill trajectory.
 Some caveats that could potentially explain this trend without our skills and abilities narrative:
 
-* Most films typically have non-elderly main characters; limiting the ability for an older, but still skillful, actor to be cast in these roles
-* Seperating an Actor's role **choice** vs their **performance** given they chose a particular role highlights the problem we see with De Niro above.
-It's quite possible that after career success and achievements actor's and directors prioritise different things (eg.
-*$Cash Money$*) in the twiglights of their careers.
+* Most films (and by extension good films) typically have non-elderly main characters; limiting the ability for an older, but still skillful, actor to be cast in these roles
+* Seperating an actor's role **choice** vs their **performance** given they chose a particular role highlights the problem we see with De Niro above.
+It's quite possible that after career success and personal skill based accolades, actor and directors prioritise different things (eg.
+**$ Cash Money $**) in the twiglight of their careers.
 

### 2017-09-04 00_utilities/create-finding-html.R

@@ -1,0 +1,19 @@
+create_finding = function(finding_text) {
+  
+  html = 
+glue::glue("<br><br><div class='finding'>
+  
+<div class='sidebar'>
+  <img src='https://github.com/TMBish/lab_posts/blob/master/00_utilities/lightbulb.png?raw=true'>
+  <span> Finding!</span>
+</div>
+
+<div class='body'> 
+  <span> {finding_text} </span> 
+</div>
+  
+</div><br><br>")
+  
+  return(html)
+  
+}

### 2017-09-04 00_utilities/highcharts-theme.R

@@ -11,8 +11,8 @@ high_tmbish = function() {
         backgroundColor = "#FDFFFC",
         style = list(
           fontFamily = base_font
-        ),
-        shadow = TRUE
+        )
+        # shadow = TRUE
       ),
       colors = list("#FF9F1C", "#2EC4B6", "#FE5F55", "#C1E1F1", "#5FEF9B"),
       title = list(
@@ -21,14 +21,14 @@ high_tmbish = function() {
       ),
       xAxis = list(
         lineWidth = 1, lineColor = "#011627",
-        gridLineWidth = 0.1, gridLineColor = "#414141", gridLineDashStyle = "LongDash",
+        gridLineWidth = 0.1, gridLineColor = "#7a7a7a", gridLineDashStyle = "LongDash",
         tickWidth = 0,
         title = list(style = header_style)
       ),
       yAxis = list(
         lineWidth = 1, lineColor = "#011627",
-        gridLineWidth = 0.1, gridLineColor = "#414141", gridLineDashStyle = "LongDash",
-        minorGridLineWidth = 0, minorGridLineColor = "#414141",
+        gridLineWidth = 0.1, gridLineColor = "#7a7a7a", gridLineDashStyle = "LongDash",
+        minorGridLineWidth = 0, minorGridLineColor = "#7a7a7a",
         # tickColor = "#011627",tickLength = 10,
         # minorTickLength = 5, minorTickWidth = 1,
         tickWidth = 0,

### 2017-09-04 01_halflife-of-acting-talent/article.Rmd
button

@@
 
-Unfortunately, because the Rotten Tomatoes development team are a bunch of politically correct SJWs, gender isn't provided on their film bio pages so we'll have to be creative.
+Unfortunately, because the Rotten Tomatoes development team are a bunch of politically correct SJWs (/s), gender isn't provided on their film bio pages so we'll have to be creative.
 The `gender` R package allows you to infer a person's gender from their first name and DOB.
@@
 
-<button class="button secondary outline" id = "update_age_series"> Show Cumulative Distribution </button>
+<button class="button w100 secondary round outline" id = "update_age_series"> Show Cumulative Distribution </button>
 

### 2017-09-04 01_halflife-of-acting-talent/article.Rmd
highcharts theme

@@
 To curate a data set for anlaysis I started with imdb user **hagennelson's** list of [top 1000 actors](http://www.imdb.com/list/ls058011111/) and imdb user **earthanime's** list of [top 250 directors](http://www.imdb.com/list/ls062419846/).
-Both lists span across generations, from the ancient (Ethel Barrymore and Alfred Hitchcock) to the modern (Chloë Grace Moretz and Christopher Nolan).
+Both lists span across generations, from the ancient (Ethel Barrymore and Alfred Hitchcock) to the modern (Chloe Grace Moretz and Christopher Nolan).
 
@@
   datatable(
-    style = 'bootstrap',
     class = 'table-hover',
@@
   datatable(
-  style = 'bootstrap',
   class = 'table-hover',
@@
 gender_props %>%
-  hw_grid(ncol = 2, rowheight = "400px") %>%
+  hw_grid(ncol = 2, rowheight = "600px") %>%
   browsable()
@@
   hc_chart(
-    animation = list(duration = 2000)
+    animation = list(duration = 2000),
+    height = 300
   ) %>%
@@
 Further - for actors - we'll have to limit the dataset to actors that played an important role in the film.
-To implement an `actor performance == film quality` approach the actors need to be influential enough to be able to affect the overall quality of the film.
+To implement an **actor performance == film quality** approach the actors need to be influential enough to be able to affect the overall quality of the film.
 So while Michael Cera's cameo in **This is the End** was high quality, it can't be said that he influenced the rotten tomatoes rating of the film on his own.
@@
 
-There's a few other things we want to control for here.
+There are few other things we want to control for here.
 I don't necessarily want to plot raw film critical rating because this might be prone to idiosyncracies within groups or ages - for example, high performing directors might generally wait until they are experienced enough to direct their first film.
 
-Instead we'll plot, for each individual and film, how well they have perfomed relative to their career average (the average tomatometer of all that individual's films).
+Instead we'll plot, for each individual and film, how well they have perfomed relative to their career average (the average tomatometer across all that individual's films).
 To illustrate this approach let's look at Denzel Washington's films.
@@
 So based on this 10 film sample Denzel had a solid early 40s where his films (**Hurricane** and **Courage Under Fire** etc) averaged a rotten tomatoes rating about 20% above his career average.
-He looks like he dropped off after 50 with a few flops like **Déjà Vu** (which I didn't mind) and **2 Guns**.
-Look I'm not calling him washed but he hasn't done anything good for a while.
+He looks like he dropped off after 50 with a few flops like **Deja Vu** (which I didn't mind) and **2 Guns**.
+Check the chart below to see how he's partially rebounded with flicks like **Flight** and **Fences**.
+
+<br>
 
@@
 
-}) %>% hw_grid(ncol = 3, rowheight = 250) %>% browsable()
+}) %>% hw_grid(ncol = 3, rowheight = 300) %>% browsable()
 
@@
 
+<br>
+
 ## The Upshot
 
-So let's extend this approach and plot out the median tomato index by age at production, giving us an idea of the *average performance above or below a career average* at each age.
+So let's extend this approach and plot out the median tomato index by age at production, giving us an idea of the **average performance above or below the career average** at each age.
 
@@
   hc_add_theme(tmbish) %>%
-  hc_chart(height = 300, spacingRight = 125, shadow=FALSE) %>%
+  hc_chart(spacingRight = 125, shadow=FALSE) %>%
   hc_xAxis(categories = rating_volumes$age_at_production, opposite = TRUE) %>%

### 2017-09-04 00_utilities/highcharts-theme.R

@@ -1,6 +1,8 @@
 high_tmbish = function() {
   
-  base_font = "Josefin Slab"
+  base_font = "Lato"
+  # base_font = "Josefin Slab"
+
   header_font = "Arvo"
   
   header_style = list(fontFamily = header_font, fontWeight = "bold", color = "#011627")
@@ -21,13 +23,13 @@ high_tmbish = function() {
       ),
       xAxis = list(
         lineWidth = 1, lineColor = "#011627",
-        gridLineWidth = 0.1, gridLineColor = "#7a7a7a", gridLineDashStyle = "LongDash",
+        gridLineWidth = 0.05, gridLineColor = "#7a7a7a", gridLineDashStyle = "LongDash",
         tickWidth = 0,
         title = list(style = header_style)
       ),
       yAxis = list(
         lineWidth = 1, lineColor = "#011627",
-        gridLineWidth = 0.1, gridLineColor = "#7a7a7a", gridLineDashStyle = "LongDash",
+        gridLineWidth = 0.05, gridLineColor = "#7a7a7a", gridLineDashStyle = "LongDash",
         minorGridLineWidth = 0, minorGridLineColor = "#7a7a7a",
         # tickColor = "#011627",tickLength = 10,
         # minorTickLength = 5, minorTickWidth = 1,

### 2017-09-04 00_utilities/highcharts-theme.R
figured out what gridlinewidth does

@@ -23,13 +23,13 @@ high_tmbish = function() {
       ),
       xAxis = list(
         lineWidth = 1, lineColor = "#011627",
-        gridLineWidth = 0.05, gridLineColor = "#7a7a7a", gridLineDashStyle = "LongDash",
+        gridLineWidth = 0.4, gridLineColor = "#7a7a7a", gridLineDashStyle = "LongDash",
         tickWidth = 0,
         title = list(style = header_style)
       ),
       yAxis = list(
         lineWidth = 1, lineColor = "#011627",
-        gridLineWidth = 0.05, gridLineColor = "#7a7a7a", gridLineDashStyle = "LongDash",
+        gridLineWidth = 0.4, gridLineColor = "#7a7a7a", gridLineDashStyle = "LongDash",
         minorGridLineWidth = 0, minorGridLineColor = "#7a7a7a",
         # tickColor = "#011627",tickLength = 10,
         # minorTickLength = 5, minorTickWidth = 1,

### 2017-09-05 00_utilities/highcharts-theme.R
Gridlines again

@@ -23,13 +23,13 @@ high_tmbish = function() {
       ),
       xAxis = list(
         lineWidth = 1, lineColor = "#011627",
-        gridLineWidth = 0.4, gridLineColor = "#7a7a7a", gridLineDashStyle = "LongDash",
+        gridLineWidth = 0.75, gridLineColor = "#7a7a7a", gridLineDashStyle = "LongDash",
         tickWidth = 0,
         title = list(style = header_style)
       ),
       yAxis = list(
         lineWidth = 1, lineColor = "#011627",
-        gridLineWidth = 0.4, gridLineColor = "#7a7a7a", gridLineDashStyle = "LongDash",
+        gridLineWidth = 0.75, gridLineColor = "#7a7a7a", gridLineDashStyle = "LongDash",
         minorGridLineWidth = 0, minorGridLineColor = "#7a7a7a",
         # tickColor = "#011627",tickLength = 10,
         # minorTickLength = 5, minorTickWidth = 1,

### 2017-09-16 01_halflife-of-acting-talent/article.Rmd
init next post

@@
 
-![Nah but actually The Intern was ok.](deniro.jpg)
+![Nah but actually The Intern was ok.](/img/lab/01/deniro.jpg)
 
 <br>
-
-<style>
-
-.finding {
-  background-color:#414141;
-  height: 125px;
-  color: #FFF;
-  display: flex;
-  align-items: center;
-  text-align:center;
-}
-
-.finding .sidebar { 
-  padding-top:15px;
-  width: 20%;
-  font-weight: bold;
-  font-size: 18px;
-}
-
-.finding .body {
-  width: 75%;
-  text-align:left;
-  font-size: 16px;
-  padding-right:10px
-}
-
-.finding .body p {
-  margin-bottom:0;
-}
-
-.finding img {
-  display : block;
-  margin : auto;
-}
-
-#snatch img {
-  height: 200px; 
-  display:block; 
-  margin: 0 auto;
-}
-
-#no-country-for-old-men img {
-  height: 200px; 
-  display:block; 
-  margin: 0 auto;
-}
-
-#the-departed img {
-  height: 200px; 
-  display:block; 
-  margin: 0 auto;
-}
-
-</style>
 
@@
 
-I then developed code (available on GitHub) to scrape data from the rotten tomatoes pages of the above individuals' films.
+I then developed code (available [here on Github](https://github.com/TMBish/lab_posts/tree/master/01_halflife-of-acting-talent/web-scrape)) to scrape data from the rotten tomatoes pages of the above individuals' films.
 The final dataset includes **12,258** films and **1,233** indviduals.
@@
 
-Let's have a look at the films data set. Click the blue `+` button to view the extra fields in the dataset (the director and top 6 actors in the film).
+Let's have a look at the films data set. Click the green `+` button to view the extra fields in the dataset (the director and top 6 actors in the film).
 
-<br>
 ```{r results='asis'}
@@
 
-<br>
-
 ```{r results='asis'}
@@
 
-To add a layer to this analysis I wanted group people by gender and film production role (actor vs director).
-So we think we'd be working with 4 groups, however, I was suprised to see that of our 250 top directors only 25 were female.
+To add a layer to this analysis I wanted to group people by gender and film production role (actor vs director).
+So we think we'd be working with 4 groups; however, I was suprised to see that of our 250 top directors only 25 were female.
 A consequence of history but appaling nonetheless.
@@
 gender_props %>%
-  hw_grid(ncol = 2, rowheight = "600px") %>%
+  hw_grid(ncol = 2, rowheight = "450px") %>%
   browsable()
@@
 Click on the male and director series to compare with the female one shown below.
-Additionally, switch between the denisty view (proportion appearing at one speicific age) and cumulative distribution view (proportion appearing at **or before** at specific age) to better understand the data.
+Additionally, switch between the density view (proportion appearing at one speicific age) and cumulative distribution view (proportion appearing at **or before** a specific age) to better understand the data.
 
@@
     animation = list(duration = 2000),
-    height = 300
+    height = 500
   ) %>%
@@
 
-![](snatch.png)
+![](/img/lab/01/snatch.png)
 
@@
 
-![](no-country-for-old-men.png)
+![](/img/lab/01/no-country-for-old-men.png)
 
@@
 
-![](the-departed.png)
+![](/img/lab/01/the-departed.png)
 
@@
 So based on this 10 film sample Denzel had a solid early 40s where his films (**Hurricane** and **Courage Under Fire** etc) averaged a rotten tomatoes rating about 20% above his career average.
-He looks like he dropped off after 50 with a few flops like **Deja Vu** (which I didn't mind) and **2 Guns**.
+He looks like he dropped off after 50 with a few flops like **Deja Vu** (which I didn't mind) and **Safe House**.
 Check the chart below to see how he's partially rebounded with flicks like **Flight** and **Fences**.
@@
 
-To help visualise this approach let's take 12 of the top 20 actors by volume and visualise average their film rating performance by age.
+To help visualise this approach let's take 12 of the top 20 actors by total number of roles in the data set and visualise average their film rating performance by age.
 De Niro is a great example of someone who starred in increasingly poor films as he got older - clearly visible in the chart below.
@@
 actors = c("Robert De Niro", "Harvey Keitel", "Christopher Walken", "Bruce Willis", "Susan Sarandon", "Jeff Bridges", "Robin Williams", "Julianne Moore", "Denzel Washington", "John Malkovich", "Meryl Streep", "Robert Redford")
+
+p = function(v) {
+  Reduce(f= function(x,y) {return(paste(y,x, sep=" <br> "))}, v)
+}
 
@@
     ) %>%
-    mutate(age_bucket = round(age_at_production / bucket) * bucket) %>%
+    mutate(
+      age_bucket = round(age_at_production / bucket) * bucket,
+      film_info = str_c(title, " <span class='", ifelse(tomatometer<=40, 'sus-tool-red', ifelse(tomatometer>75, 'sus-tool-green', 'sus-tool-amber')) ,"'>", tomatometer, "% </span>")      
+    ) %>%
     group_by(age_bucket) %>%
+    arrange(tomatometer) %>%
     summarise(
-      index = mean(tomato_index),
-      films = n()) %>%
+      y = mean(tomato_index),
+      films = n(),
+      tooltip = p(film_info)
+    ) %>%
     filter(films >= 3)
@@
       type = "spline",
-      data = actordata$index
+      data = list_parse(actordata %>% select(y, tooltip))
     ) %>%
@@
     hc_tooltip(
-         formatter = JS("function(){return('<b>Tomato Index: </b>' + Math.round(this.y*1000) / 10 +'%' )}")
+         formatter = JS("function(){return('<div style=\"text-align:right;\">' + this.point.tooltip + '</div>')}"),
+         useHTML = TRUE,
+         style = list(textalign = "right")
     )
@@
   hc_yAxis(
-    title = list(text = "Probablity Density"),
+    title = list(text = "Median Tomato Index"),
     min = -0.4,
@@
 
-* Most films (and by extension good films) typically have non-elderly main characters; limiting the ability for an older, but still skillful, actor to be cast in these roles
+* Most films (and by extension good films) typically have non-elderly main characters; limiting the ability for an older, but still skillful, actor to be cast in these roles.
 * Seperating an actor's role **choice** vs their **performance** given they chose a particular role highlights the problem we see with De Niro above.
@@
 
-All we can say for sure is that the prime of your acting life (the quality of the films you're in) happens between 27-35.
+All we can say for sure is that the prime of your acting life - defined by the quality of the films you're appear in - happens between 27-35.
 Whether that's becuase you were at the peak of your abilities, or you were more likely to be seeking critically acclaimed roles (hunting that first Oscar), or you were just given opportunities you wouldn't be afforded later in life we'll have to leave to another day.
+To spend more time exploring film data head over to my film data shiny app [Stratton](http://www.tmbish.me/shiny/stratton/) in the Shiny section of my website.
 

### 2017-09-16 02_rmarkdown-interactivity/post.Rmd
Added initial prob distribution dataset

---
title: "Adding Interactivity to Static Rmarkdown Documents"
author: ~
date: "`r Sys.time()`"
day: "`r format(Sys.Date(), '%d')`"
month: "`r format(Sys.Date(), '%b')`"
year: "`r format(Sys.Date(), '%Y')`"
slug: adding-rmarkdown-interactivity
categories: []
tags: ["R", "R Markdown", "Javascript", "Highcharts"]
highlight: "kate"
description: "Interactivity can be added to static HTML R Markdown outputs by using a couple of cool tricks."
img: "bulletin-edition-1"
---

# Generate Data

```{r}
library(dplyr)
library(tidyr)

data <- data.frame(
  normal = rnorm(10000, 5, 2), # 1000 random from normal dist
  exponential = rexp(10000, 0.5), # 1000 random from exponential dist
  uniform = runif(10000, 0, 10) # 1000 random from uniform dist
)

# Data Manipulation
data %>%
  gather(distribution, value, normal:uniform) %>%
  mutate(value = value %>% round(1)) %>%
  filter(value >= 0, value <= 12) %>%
  group_by(distribution, value) %>%
  summarise(points = n()) %>%
  ungroup() %>% group_by(distribution) %>%
  mutate(density = points / sum(points)) %>%
  ungroup() %>%
  select(-points) -> density

```

# Plot Data

```{r}

library(highcharter)

plot_data = density %>% spread(distribution, density)

  highchart() %>%
  hc_add_theme(hc_theme_monokai()) %>%
  hc_chart(
    animation = list(duration = 2000),
    height = 500
  ) %>%
  hc_xAxis(
    categories = plot_data$value,
    title = list(text = "Value")
  ) %>%
  hc_yAxis(
    title = list(text = "Probablity Density"),
    labels = list(formatter = JS("function(){return(Math.round(this.value * 1000) / 10 + '%')}"))
  ) %>%
  hc_title(text = "3 Probability Densities") %>%
  hc_add_series(
    name = "Normal", 
    type = "spline",
    data = plot_data$normal,
    marker = list(enabled = FALSE)
  ) %>%
  hc_add_series(
    name = "Exponential",
    type = "spline",
    data = plot_data$exponential,
    marker = list(enabled = FALSE)
  ) %>%
  hc_add_series(
    name = "Uniform",
    type = "spline",
    data = plot_data$uniform,
    marker = list(enabled = FALSE)
  )

```

# Add Interactivity

```{class.source="language-javascript"}

$(document).ready(function() {

  var show_cdf = false;

  $("#update_age_series").click(function(){

    var chart=$("#age_series_chart").find(".highchart").highcharts();

    if (show_cdf) {

      chart.yAxis[0].setExtremes(0,null);
      chart.yAxis[0].setTitle({text:"Probability Density", redraw:false});
      #dir_pdf = `r dir_pdf`;
      #female_pdf = `r female_pdf`;
      #male_pdf = `r male_pdf`;
      chart.series[0].setData(dir_pdf);
      chart.series[1].setData(male_pdf);
      chart.series[2].setData(female_pdf);
      $("#update_age_series").html("Show Cumulative Distribution");

    } else {

      chart.yAxis[0].setExtremes(0,1);
      chart.yAxis[0].setTitle({text:"Cumulative Probability", redraw:false});
      #dir_cdf = `r dir_cdf`;
      #female_cdf = `r female_cdf`;
      #male_cdf = `r male_cdf`;
      chart.series[0].setData(dir_cdf);
      chart.series[1].setData(male_cdf);
      chart.series[2].setData(female_cdf);

      $("#update_age_series").html("Show Density");

  };

  show_cdf = !show_cdf

  }); 
});

```

### 2017-09-17 02_rmarkdown-interactivity/post.Rmd
Progress on rmarkdown interactivity

@@
 ---
+
+# Overview
+
+Interactivity in data analytics outputs is great for a number of reasons.
+
+As an R User you have a number of different formats to write. It can become confusing about how each of these formats differ from one another, specifically when it comes to interactivity.
+
+- **Shiny Apps** is the most interactive format with few limitations but requires a server to run.
+- **HTML R markdown docs, slides and Notebooks** are nice comprimise.
+- **Non-HTML Rmarkdown outputs** are the least interactive with text and plots (images) assembled in a static arrangement.
+
+This post specifically focuses on option 2 and how it can be enhanced to be more like '
 
@@
 
+density %>% head()
+
 ```
@@
   hc_xAxis(
-    categories = plot_data$value,
     title = list(text = "Value")
@@
     type = "spline",
-    data = plot_data$normal,
+    data = plot_data %>% select(x = value, y = normal) %>% list_parse()
+    #marker = list(enabled = FALSE)
+  ) %>%
+  hc_add_series(
+    name = "Exponential",
+    type = "spline",
+    data = plot_data %>% select(x = value, y = exponential) %>% list_parse()
+   # marker = list(enabled = FALSE)
+  ) %>%
+  hc_add_series(
+    name = "Uniform",
+    type = "spline",
+    data = plot_data %>% select(x = value, y = uniform) %>% list_parse()
+   # marker = list(enabled = FALSE)
+  ) -> chart
+
+chart
+
+```
+
+# Add Interactivity
+
+```{r}
+
+# Get CDF from density dataframe
+get_dist = function(df, var, type) {
+
+  if (type=="pdf") {
+
+   df %>%
+    filter(distribution == !!var) %>% # Tidy Evaluation
+    mutate(
+      js_pair = paste0("[", value, "," , density %>% round(6), "]")
+    ) %>%
+    pull(js_pair) %>% # Just found this function, handy!
+    return()
+
+  } else {
+
+   df %>%
+    filter(distribution == !!var) %>% # Tidy Evaluation
+    arrange(value) %>%
+    mutate(
+      cdf = cumsum(density),
+      js_pair = paste0("[", value, "," , cdf %>% round(4), "]")
+    ) %>%
+    pull(js_pair) %>% # Just found this function, handy!
+    return()
+
+  }
+
+}
+
+# Conver R char vector of x, y pairs to JS array string
+js_stringify = function(vec) {
+
+  vec %>%
+    paste(collapse = ",") %>%
+    paste0("[", . , "]") %>%
+    JS() %>%
+    return()
+
+}
+
+# Javascriptise PDF Data
+nor_pdf = get_dist(density, "normal", "pdf") %>% js_stringify()
+exp_pdf = get_dist(density, "exponential", "pdf") %>% js_stringify()
+uni_pdf = get_dist(density, "uniform", "pdf") %>% js_stringify()
+
+# Javascriptise CDF Data
+nor_cdf = get_dist(density, "normal", "cdf") %>% js_stringify()
+exp_cdf = get_dist(density, "exponential", "cdf") %>% js_stringify()
+uni_cdf = get_dist(density, "uniform", "cdf") %>% js_stringify()
+
+```
+
+# In action
+
+```{r}
+
+  highchart(elementId = "densities_v2") %>%
+  hc_add_theme(hc_theme_monokai()) %>%
+  hc_chart(
+    animation = list(duration = 2000),
+    height = 500
+  ) %>%
+  hc_xAxis(
+    #categories = plot_data$value,
+    title = list(text = "Value")
+  ) %>%
+  hc_yAxis(
+    title = list(text = "Probablity Density"),
+    labels = list(formatter = JS("function(){return(Math.round(this.value * 1000) / 10 + '%')}"))
+  ) %>%
+  hc_title(text = "3 Probability Densities") %>%
+  hc_add_series(
+    name = "Normal", 
+    type = "spline",
+    #data = plot_data$normal,
+    data = plot_data %>% select(x = value, y = normal) %>% list_parse(),
     marker = list(enabled = FALSE)
@@
     type = "spline",
-    data = plot_data$exponential,
+    #data = plot_data$exponential,
+    data= plot_data %>% select(x = value, y = exponential) %>% list_parse(),
     marker = list(enabled = FALSE)
@@
     type = "spline",
-    data = plot_data$uniform,
+    #data = plot_data$uniform,
+    data = plot_data %>% select(x = value, y = uniform) %>% list_parse(),
     marker = list(enabled = FALSE)
@@
 
-# Add Interactivity
+<button id="test"> Click Me </button>
+
+<script>
+
+  $(document).ready(function() {
+
+    var show_cdf = true;
+
+    $("#test").click(function(){
+
+      var chart=$("#densities_v2").highcharts();
+
+      if (!show_cdf) {
+
+        chart.yAxis[0].setTitle({text:"Cumulative Probability", redraw:false});
+        uni_cdf = `r uni_cdf`;
+        nor_cdf = `r nor_cdf`;
+        exp_cdf = `r exp_cdf`;
+        chart.series[0].setData(nor_cdf);
+        chart.series[1].setData(exp_cdf);
+        chart.series[2].setData(uni_cdf);
+        $("#test").html("Show Density");
+
+      } else {
+
+        chart.yAxis[0].setTitle({text:"Probability Density", redraw:false});
+        uni_pdf = `r uni_pdf`;
+        nor_pdf = `r nor_pdf`;
+        exp_pdf = `r exp_pdf`;
+        chart.series[0].setData(nor_pdf);
+        chart.series[1].setData(exp_pdf);
+        chart.series[2].setData(uni_pdf);
+        $("#test").html("Show CDF");
+
+    };
+
+    show_cdf = !show_cdf;
+
+    }); 
+  });
+
+</script>
 
@@
 
-  $("#update_age_series").click(function(){
+  $("#test").click(function(){
 
-    var chart=$("#age_series_chart").find(".highchart").highcharts();
+    var chart=$("#densities_v2").find(".highchart").highcharts();
 
@@
       chart.yAxis[0].setTitle({text:"Probability Density", redraw:false});
-      #dir_pdf = `r dir_pdf`;
-      #female_pdf = `r female_pdf`;
-      #male_pdf = `r male_pdf`;
-      chart.series[0].setData(dir_pdf);
-      chart.series[1].setData(male_pdf);
-      chart.series[2].setData(female_pdf);
-      $("#update_age_series").html("Show Cumulative Distribution");
+      uni_cdf = `r uni_cdf`;
+      nor_cdf = `r nor_cdf`;
+      exp_cdf = `r exp_cdf`;
+      chart.series[0].setData(uni_cdf);
+      chart.series[1].setData(nor_cdf);
+      chart.series[2].setData(exp_cdf);
 
@@
       chart.yAxis[0].setTitle({text:"Cumulative Probability", redraw:false});
-      #dir_cdf = `r dir_cdf`;
-      #female_cdf = `r female_cdf`;
-      #male_cdf = `r male_cdf`;
-      chart.series[0].setData(dir_cdf);
-      chart.series[1].setData(male_cdf);
-      chart.series[2].setData(female_cdf);
 

### 2017-09-20 02_rmarkdown-interactivity/post.Rmd
Progress on rmarkdown post

@@
 
-Interactivity in data analytics outputs is great for a number of reasons.
+Adding interactivity to data analytics outputs is a great tool to have in your toolkit.
 
-As an R User you have a number of different formats to write. It can become confusing about how each of these formats differ from one another, specifically when it comes to interactivity.
+As an R User you generally have a few major output options. However, it's not immediately obvious how interactive you can get within each format.
 
-- **Shiny Apps** is the most interactive format with few limitations but requires a server to run.
-- **HTML R markdown docs, slides and Notebooks** are nice comprimise.
-- **Non-HTML Rmarkdown outputs** are the least interactive with text and plots (images) assembled in a static arrangement.
+- **Shiny Apps** are the most interactive format with few limitations but require a computer server to host. This can be too much overhead for smaller tasks.
+- **Non-HTML Rmarkdown outputs** aren't very interactive. Text, plots and other outputs are statically assembled at runtime and the document stays that way.
+- **HTML R markdown outputs** are a nice comprimise.
+They support superficially interactive elements (tooltips, action filtering) through HTML widgets.
+**AND** interactivity can be enhanced and that's the topic of this post!
 
-This post specifically focuses on option 2 and how it can be enhanced to be more like '
+The key concept to get your head around is the client / server model from web-development.
+The upshot here is that if you don't have a server (an engine to drive what content is shown) your interactivity is always limited.
+I can request my R markdown document to go and retrieve 10 extra rows from the database cause there's no one there to listen to me.
+Everything you allow the person (client) to see must be delivered to them when they open the document.
+The key to unlock interactivity in this context is with `htmlwidgets` and client side javascript.
 
 # Generate Data
+
+I'll create a toy example with the awesome `highcharter` package.
+Our aim will be to allow the user to switch between a view of probability density functions and cumulative distribution functions.
+If you forget the difference, don't worry it's not important.
 
@@
 plot_data = density %>% spread(distribution, density)
+# 
+#   highchart() %>%
+#   hc_add_theme(hc_theme_monokai()) %>%
+#   hc_chart(
+#     animation = list(duration = 2000),
+#     height = 500
+#   ) %>%
+#   hc_xAxis(
+#     title = list(text = "Value")
+#   ) %>%
+#   hc_yAxis(
+#     title = list(text = "Probablity Density"),
+#     labels = list(formatter = JS("function(){return(Math.round(this.value * 1000) / 10 + '%')}"))
+#   ) %>%
+#   hc_title(text = "3 Probability Densities") %>%
+#   hc_add_series(
+#     name = "Normal", 
+#     type = "spline",
+#     data = plot_data %>% select(x = value, y = normal) %>% list_parse()
+#     #marker = list(enabled = FALSE)
+#   ) %>%
+#   hc_add_series(
+#     name = "Exponential",
+#     type = "spline",
+#     data = plot_data %>% select(x = value, y = exponential) %>% list_parse()
+#    # marker = list(enabled = FALSE)
+#   ) %>%
+#   hc_add_series(
+#     name = "Uniform",
+#     type = "spline",
+#     data = plot_data %>% select(x = value, y = uniform) %>% list_parse()
+#    # marker = list(enabled = FALSE)
+#   ) -> chart
+# 
+# chart
 
-  highchart() %>%
-  hc_add_theme(hc_theme_monokai()) %>%
-  hc_chart(
-    animation = list(duration = 2000),
-    height = 500
-  ) %>%
-  hc_xAxis(
-    title = list(text = "Value")
-  ) %>%
-  hc_yAxis(
-    title = list(text = "Probablity Density"),
-    labels = list(formatter = JS("function(){return(Math.round(this.value * 1000) / 10 + '%')}"))
-  ) %>%
-  hc_title(text = "3 Probability Densities") %>%
-  hc_add_series(
-    name = "Normal", 
-    type = "spline",
-    data = plot_data %>% select(x = value, y = normal) %>% list_parse()
-    #marker = list(enabled = FALSE)
-  ) %>%
-  hc_add_series(
-    name = "Exponential",
-    type = "spline",
-    data = plot_data %>% select(x = value, y = exponential) %>% list_parse()
-   # marker = list(enabled = FALSE)
-  ) %>%
-  hc_add_series(
-    name = "Uniform",
-    type = "spline",
-    data = plot_data %>% select(x = value, y = uniform) %>% list_parse()
-   # marker = list(enabled = FALSE)
-  ) -> chart
-
-chart
+hchart(density, "spline", hcaes(x = value, y = density, group = distribution))
 

### 2017-09-21 02_rmarkdown-interactivity/post.Rmd
More content on this post

--- 2017-09-16 02_rmarkdown-interactivity/post.Rmd
@@
 
+# Overview
+
+Adding interactivity to data analytics outputs is a great tool to have in your toolkit.
+
+As an R User you have a few major output formats to choose from. However, it's not immediately obvious how much interactivity you can embed within each format.
+
+- **Shiny Apps** are the most interactive format with few limitations but require a computer server to host. This can be too much overhead for smaller tasks.
+- **Non-HTML Rmarkdown outputs** aren't very interactive. Text, plots and other outputs are statically assembled at runtime and the document stays that way.
+- **HTML R markdown outputs** are a nice comprimise.
+They support superficially interactive elements (tooltips, action filtering) through HTML widgets **AND** if you know a few tricks interactivity can be signficantly enhanced.
+That's the topic of this post!
+
+The key concept to get your head around is the client / server model from web-development.
+The upshot here is that if you don't have a server (an engine to drive what content is shown to the user) your interactivity will always limited.
+I can't request my R markdown document to go and retrieve 10 extra rows from a database because there's no one actually there to listen to me - the lights aren't on.
+Everything you allow the person (client) to see must be delivered to them when they open the document.
+The key tools to unlock interactivity in this context are `htmlwidgets` and client side javascript.
+
 # Generate Data
+
+I'll create a toy example with the awesome `highcharter` package.
+Our aim will be to allow the user to switch between a view of probability density functions and cumulative distribution functions.
+If you forget the difference, don't worry it's not important.
 
@@
 library(tidyr)
+library(highcharter)
 
@@
 
-plot_data = density %>% spread(distribution, density)
-
-  highchart() %>%
+hchart(density, "spline", hcaes(x = value, y = density, group = distribution)) %>%
+  hc_elementId(id = "static_graph") %>%
   hc_add_theme(hc_theme_monokai()) %>%
@@
   ) %>%
-  hc_title(text = "3 Probability Densities") %>%
-  hc_add_series(
-    name = "Normal", 
-    type = "spline",
-    data = plot_data$normal,
-    marker = list(enabled = FALSE)
-  ) %>%
-  hc_add_series(
-    name = "Exponential",
-    type = "spline",
-    data = plot_data$exponential,
-    marker = list(enabled = FALSE)
-  ) %>%
-  hc_add_series(
-    name = "Uniform",
-    type = "spline",
-    data = plot_data$uniform,
-    marker = list(enabled = FALSE)
-  )
+  hc_title(text = "3 Probability Densities")
 
@@
 # Add Interactivity
+
+```{r}
+
+# Get CDF from density dataframe
+get_dist = function(df, var, type) {
+
+  if (type=="pdf") {
+
+   df %>%
+    filter(distribution == !!var) %>% # Tidy Evaluation
+    mutate(
+      js_pair = paste0("[", value, "," , density %>% round(6), "]")
+    ) %>%
+    pull(js_pair) %>% # Just found this function, handy!
+    return()
+
+  } else {
+
+   df %>%
+    filter(distribution == !!var) %>% # Tidy Evaluation
+    arrange(value) %>%
+    mutate(
+      cdf = cumsum(density),
+      js_pair = paste0("[", value, "," , cdf %>% round(4), "]")
+    ) %>%
+    pull(js_pair) %>% # Just found this function, handy!
+    return()
+
+  }
+
+}
+
+# Conver R char vector of x, y pairs to JS array string
+js_stringify = function(vec) {
+
+  vec %>%
+    paste(collapse = ",") %>%
+    paste0("[", . , "]") %>%
+    JS() %>%
+    return()
+
+}
+
+# Javascriptise PDF Data
+nor_pdf = get_dist(density, "normal", "pdf") %>% js_stringify()
+exp_pdf = get_dist(density, "exponential", "pdf") %>% js_stringify()
+uni_pdf = get_dist(density, "uniform", "pdf") %>% js_stringify()
+
+# Javascriptise CDF Data
+nor_cdf = get_dist(density, "normal", "cdf") %>% js_stringify()
+exp_cdf = get_dist(density, "exponential", "cdf") %>% js_stringify()
+uni_cdf = get_dist(density, "uniform", "cdf") %>% js_stringify()
+
+```
+
+# In action
+
+```{r}
+hchart(density, "spline", hcaes(x = value, y = density, group = distribution)) %>%
+  hc_elementId(id = "interactive_graph") %>%
+  hc_add_theme(hc_theme_monokai()) %>%
+  hc_chart(
+    animation = list(duration = 2000),
+    height = 500
+  ) %>%
+  hc_xAxis(
+    title = list(text = "Value")
+  ) %>%
+  hc_yAxis(
+    title = list(text = "Probablity Density"),
+    labels = list(formatter = JS("function(){return(Math.round(this.value * 1000) / 10 + '%')}"))
+  ) %>%
+  hc_title(text = "3 Probability Densities")
+
+```
+
+<button id="test"> Click Me </button>
+
+<script>
+
+  $(document).ready(function() {
+
+    var show_cdf = false;
+
+    $("#test").click(function(){
+
+      var chart=$("#interactive_graph").highcharts();
+
+      if (!show_cdf) {
+
+        chart.yAxis[0].setTitle({text:"Cumulative Probability", redraw:false});
+
+        for (var i = 0; i <= chart.series.length; i++) {
+
+          if (chart.series[i].name=="normal") {
+            new_data = `r nor_cdf`;
+          } else if (chart.series[i].name=="uniform") {
+            new_data = `r uni_cdf`;
+          } else {
+            new_data = `r exp_cdf`;
+          }
+
+          chart.series[i].setData(new_data);
+
+        }
+
+        $("#test").html("Show Density");
+
+      } else {
+
+        chart.yAxis[0].setTitle({text:"Probability Density", redraw:false});
+
+        for (var i = 0; i <= chart.series.length; i++) {
+
+          if (chart.series[i].name=="normal") {
+            new_data = `r nor_pdf`;
+          } else if (chart.series[i].name=="uniform") {
+            new_data = `r uni_pdf`;
+          } else {
+            new_data = `r exp_pdf`;
+          }
+
+          chart.series[i].setData(new_data);
+
+        }
+
+        $("#test").html("Show CDF");
+
+    };
+
+    show_cdf = !show_cdf;
+
+    }); 
+  });
+
+</script>
 
@@
 
-  $("#update_age_series").click(function(){
+    $("#test").click(function(){
 
-    var chart=$("#age_series_chart").find(".highchart").highcharts();
+      var chart=$("#interactive_graph").highcharts();
 
-    if (show_cdf) {
+      if (!show_cdf) {
 
-      chart.yAxis[0].setExtremes(0,null);
-      chart.yAxis[0].setTitle({text:"Probability Density", redraw:false});
-      #dir_pdf = `r dir_pdf`;
-      #female_pdf = `r female_pdf`;
-      #male_pdf = `r male_pdf`;
-      chart.series[0].setData(dir_pdf);
-      chart.series[1].setData(male_pdf);
-      chart.series[2].setData(female_pdf);
-      $("#update_age_series").html("Show Cumulative Distribution");
+        chart.yAxis[0].setTitle({text:"Cumulative Probability", redraw:false});
+
+        for (var i = 0; i <= chart.series.length; i++) {
+
+          if (chart.series[i].name=="normal") {
+            new_data = `r nor_cdf`;
+          } else if (chart.series[i].name=="uniform") {
+            new_data = `r uni_cdf`;
+          } else {
+            new_data = `r exp_cdf`;
+          }
+
+          chart.series[i].setData(new_data);
+
+        }
+
+        $("#test").html("Show Density");
 
@@
 
-      chart.yAxis[0].setExtremes(0,1);
-      chart.yAxis[0].setTitle({text:"Cumulative Probability", redraw:false});
-      #dir_cdf = `r dir_cdf`;
-      #female_cdf = `r female_cdf`;
-      #male_cdf = `r male_cdf`;
-      chart.series[0].setData(dir_cdf);
-      chart.series[1].setData(male_cdf);
-      chart.series[2].setData(female_cdf);
+        chart.yAxis[0].setTitle({text:"Probability Density", redraw:false});
 
-      $("#update_age_series").html("Show Density");
+        for (var i = 0; i <= chart.series.length; i++) {
+
+          if (chart.series[i].name=="normal") {
+            new_data = `r nor_pdf`;
+          } else if (chart.series[i].name=="uniform") {
+            new_data = `r uni_pdf`;
+          } else {
+            new_data = `r exp_pdf`;
+          }
+
+          chart.series[i].setData(new_data);
+
+        }
+
+        $("#test").html("Show CDF");
 
@@
 
-  show_cdf = !show_cdf
+    show_cdf = !show_cdf;
 

### 2017-10-31 02_rmarkdown-interactivity/post.Rmd
lab post progress

@@
 
+```{r}
+# Knitr Options
+knitr::opts_chunk$set(warning=FALSE, message=FALSE, strip.white = FALSE)
+
+```
+
 # Overview
@@
 
-- **Shiny Apps** are the most interactive format with few limitations but require a computer server to host. This can be too much overhead for smaller tasks.
+- **Shiny Apps** are the most interactive format with few limitations but require a computer server to host as well as codifying a decent amount of interactivity logic in the shiny syntax.
+This can be too much overhead for smaller tasks.
 - **Non-HTML Rmarkdown outputs** aren't very interactive. Text, plots and other outputs are statically assembled at runtime and the document stays that way.
@@
 
-# Generate Data
+# Example
 
@@
 
-```{r}
+**Generate Data**
+```{r message=FALSE, warning=FALSE}
 library(dplyr)
@@
 
-# Plot Data
+Using `highcharter` we'll plot the densities of these 3 distributions.
 
+**Plot Data**
 ```{r}
@@
   hc_add_theme(hc_theme_monokai()) %>%
-  hc_chart(
-    animation = list(duration = 2000),
-    height = 500
-  ) %>%
-  hc_xAxis(
-    title = list(text = "Value")
-  ) %>%
+  hc_chart(height = 500) %>%
+  hc_xAxis(title = list(text = "Value")) %>%
   hc_yAxis(
@@
     ) %>%
-    pull(js_pair) %>% # Just found this function, handy!
+    pull(js_pair) %>% # Extract column as vector
     return()

### 2017-11-19 02_rmarkdown-interactivity/post.Rmd
progress

@@
 
-- **Shiny Apps** are the most interactive format with few limitations but require a computer server to host as well as codifying a decent amount of interactivity logic in the shiny syntax.
+- **Shiny Apps** are the most interactive format with few limitations but require a computer server to host as well as codifying a decent amount of the interactivity logic in  shiny syntax.
 This can be too much overhead for smaller tasks.
@@
 The key concept to get your head around is the client / server model from web-development.
-The upshot here is that if you don't have a server (an engine to drive what content is shown to the user) your interactivity will always limited.
+The upshot here is that if you don't have a server (an engine to drive what content is shown to the user) your interactivity will always be limited.
 I can't request my R markdown document to go and retrieve 10 extra rows from a database because there's no one actually there to listen to me - the lights aren't on.
@@
 
-I'll create a toy example with the awesome `highcharter` package.
+I'll create a toy example with the awesome `highcharter` package - a wrapper for the Highcharts API.
 Our aim will be to allow the user to switch between a view of probability density functions and cumulative distribution functions.
@@
 
-Using `highcharter` we'll plot the densities of these 3 distributions.
+**Plot Data**
 
-**Plot Data**
+Using `highcharter` we'll plot the empirical densities of our sample from these 3 distributions.
+
 ```{r}
-
 library(highcharter)
@@
   hc_elementId(id = "static_graph") %>%
-  hc_add_theme(hc_theme_monokai()) %>%
+  hc_add_theme(hc_theme_538()) %>%
   hc_chart(height = 500) %>%
@@
   ) %>%
-  hc_title(text = "3 Probability Densities")
+  hc_title(text = "3 Probability Densities") %>% 
+  hc_subtitle(text = "Emprical density plot for a 10,000 random sample from each of uniform, normal and exponential probability distributions.")
 
@@
 
-# Add Interactivity
+# Preparing Data
+
+The next thing we're going to do is to create a function that can extract the probability densities and the cumulative probability densities (just taking a cumulative sum over the density column) from our simulated and aggregated data set from above.
 
@@
 }
+```
 
-# Conver R char vector of x, y pairs to JS array string
+Now what we want, and moving ahead a little bit, is to create a function that will convert the output of the above function (a simple numeric R vector) and create a valid javascript array.
+We need to do this because we're going to embed the 6 key data sets into client side javascript code.
+The `JS` function from `htmlwidgets` attaches the required metadata to a string so that it is interpreted as javascript code intstead of a simple string.
+
+```{r}
+# Convert R char vector of x, y pairs to JS array string
 js_stringify = function(vec) {
@@
 }
+```
 
+Now we'll create those 6 key javascript arrays.
+
+```{r}
 # Javascriptise PDF Data

### 2017-11-19 02_rmarkdown-interactivity/post.Rmd
More progress

@@
 
-**Plot Data**
+## Plot Data
 
@@
   ) %>%
-  hc_title(text = "3 Probability Densities") %>% 
+  hc_title(text = "Probability Densities: Uniform, Normal, and Exponential") %>% 
   hc_subtitle(text = "Emprical density plot for a 10,000 random sample from each of uniform, normal and exponential probability distributions.")
@@
 
-# Preparing Data
+## Preparing Data
 
@@
 
-Now we'll create those 6 key javascript arrays.
+Now we'll use both of those functions to create our 6 key javascript arrays.
 
@@
 
-# In action
+## The Javascript
+
+Now what we have to do is write some - relatively simple - javascript to switch CDF and PDF data when the user presses a button.
+
+The key things to call out in this code are:
+* thing 1
+* The `show_cdf` boolean keeps track of which view to switch out
+* To find the `highcharts` object within the page you can use the `.highcharts()`
+* More things
+
+```{class.source="language-javascript"}
+
+  $(document).ready(function() {
+
+    var show_cdf = false;
+
+    $("#test").click(function(){
+
+      var chart=$("#interactive_graph").highcharts();
+
+      if (!show_cdf) {
+
+        chart.yAxis[0].setTitle({text:"Cumulative Probability", redraw:false});
+
+        for (var i = 0; i <= chart.series.length; i++) {
+
+          if (chart.series[i].name=="normal") {
+            new_data = `r nor_cdf`;
+          } else if (chart.series[i].name=="uniform") {
+            new_data = `r uni_cdf`;
+          } else {
+            new_data = `r exp_cdf`;
+          }
+
+          chart.series[i].setData(new_data);
+
+        }
+
+        $("#test").html("Show Density");
+
+      } else {
+
+        chart.yAxis[0].setTitle({text:"Probability Density", redraw:false});
+
+        for (var i = 0; i <= chart.series.length; i++) {
+
+          if (chart.series[i].name=="normal") {
+            new_data = `r nor_pdf`;
+          } else if (chart.series[i].name=="uniform") {
+            new_data = `r uni_pdf`;
+          } else {
+            new_data = `r exp_pdf`;
+          }
+
+          chart.series[i].setData(new_data);
+
+        }
+
+        $("#test").html("Show CDF");
+
+    };
+
+    show_cdf = !show_cdf;
+
+    }); 
+  });
+
+```
+
+## In Action
+
+Now let's see why we went to all that effort.
 
 ```{r}
+
 hchart(density, "spline", hcaes(x = value, y = density, group = distribution)) %>%
   hc_elementId(id = "interactive_graph") %>%
-  hc_add_theme(hc_theme_monokai()) %>%
+  hc_add_theme(hc_theme_538()) %>%
   hc_chart(
@@
   ) %>%
-  hc_xAxis(
-    title = list(text = "Value")
-  ) %>%
+  hc_xAxis(title = list(text = "Value")) %>%
   hc_yAxis(
@@
   ) %>%
-  hc_title(text = "3 Probability Densities")
+  hc_title(text = "Probability Distributions: Uniform, Normal, and Exponential") %>% 
+  hc_subtitle(text = "Emprical density plot for a 10,000 random sample from each of uniform, normal and exponential probability distributions.")
 
@@
 <button id="test"> Click Me </button>
+
+<br>
+<br>
 
@@
 </script>
-
-```{class.source="language-javascript"}
-
-  $(document).ready(function() {
-
-    var show_cdf = false;
-
-    $("#test").click(function(){
-
-      var chart=$("#interactive_graph").highcharts();
-
-      if (!show_cdf) {
-
-        chart.yAxis[0].setTitle({text:"Cumulative Probability", redraw:false});
-
-        for (var i = 0; i <= chart.series.length; i++) {
-
-          if (chart.series[i].name=="normal") {
-            new_data = `r nor_cdf`;
-          } else if (chart.series[i].name=="uniform") {
-            new_data = `r uni_cdf`;
-          } else {
-            new_data = `r exp_cdf`;
-          }
-
-          chart.series[i].setData(new_data);
-
-        }
-
-        $("#test").html("Show Density");
-
-      } else {
-
-        chart.yAxis[0].setTitle({text:"Probability Density", redraw:false});
-
-        for (var i = 0; i <= chart.series.length; i++) {
-
-          if (chart.series[i].name=="normal") {
-            new_data = `r nor_pdf`;
-          } else if (chart.series[i].name=="uniform") {
-            new_data = `r uni_pdf`;
-          } else {
-            new_data = `r exp_pdf`;
-          }
-
-          chart.series[i].setData(new_data);
-
-        }
-
-        $("#test").html("Show CDF");
-
-    };
-
-    show_cdf = !show_cdf;
-
-    }); 
-  });
-
-```

### 2018-12-13 04_highcharter-handbook/highcharter-handbook.Rmd
Init highcharter handbook

---
title: "Highcharter Handbook"
author: "Tom Bishop"
date: "29 November 2018"
output: 
    hrbrthemes::ipsum:
        self_contained: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

This is an R Markdown document. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document. You can embed an R code chunk like this:

```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.

### 2019-07-30 04_highcharter-handbook/highcharter-handbook.Rmd
Started back working on HC handbook

@@
 author: "Tom Bishop"
-date: "29 November 2018"
+date: "30 July 2019"
 output: 
-    hrbrthemes::ipsum:
-        self_contained: yes
+    html_document:
+        toc: true
+        toc_float: true        
+        theme: sandstone
 ---
@@
 ```{r setup, include=FALSE}
+
+library(highcharter)
+library(tidyverse)
 knitr::opts_chunk$set(echo = TRUE)
@@
 
-## R Markdown
+## Overview
+
+`highcharter` is an R implementation of the highcharts javascript graphing API through R's `htmlwidgets`.
+Most of the highcharts functionality is implemented through `highcharter` however the documentation is somewhat limited.
+This guide will provide examples on how to create and customise various graphs whilst providing some tips on how to think about the package that will help you build and debug your charts.
+
+Your most important resource should be the highcharts api documentation which you should bookmark in your browser:
+
+* [Highcharts API Documentation](https://api.highcharts.com/highcharts/)
+
+Using `highcharter` properly will involve learning a little javascript but not too much, and it's probably good for you.
+
+## Basics
+
+```{r}
+hchart(starwars, "column", hcaes(x = name, y = height))
+```
+
+There's a number of things you might notice about this chart if you've spent a bit of time graphing in R.
+First thing is that if you can interact with it; hover over it to see a (relatively ugly) tooltip.
+Second is that it's dynamic, which you'll notice initially because there are more bars (star wars characters) than there are labels on the y-axis.
+To see an exaggerated version of this reduce the width of your browser window to see the chart react and replot as it tries to estimate the best way to present the data without it looking busy and cluttered; the number of characters shown on the y-axis will keep decreasing.
+
+This is normally a great and useful feature of highcharts but it's something to keep track of as you plot.
+
+## hchart()
+
+The `hchart()` function is kind of an amazing function that has been written to create immediate logical graphs from various types of R objects.
+`hchart()` will detect the R object type and decide the best way to plot it.
+Here are some examples.
+Notice that the function call is exactly the same `hchart([object])` but the plot that's produced is very different.
+
+### Numeric Vector -> Histogram
+
+```{r}
+starwars %>%
+  pull(mass) %>%
+  hchart()
+```
+
+### R Density Object -> Density Plot
+
+```{r}
+starwars %>%
+  filter(!is.na(mass)) %>%
+  pull(mass) %>%
+  density() %>%
+  hchart()
+```
+
+### Forecast Object -> Timeseries / Forecast Chart
+
+## Links
 

### 2019-08-09 04_highcharter-handbook/highcharter-handbook.Rmd
HC handbook update

@@
 library(tidyverse)
+library(forecast)
 knitr::opts_chunk$set(echo = TRUE)
@@
 
-## Basics
+## Datasets
+
+I'll frequently be using the following two datasets:
+
+* dplyr::starwars | the physical traits and info for characters in the starwars films
+* dplyr::storms | hurricane timeseries data
+
+## hchart()
+
+The `hchart()` function is kind of an amazing function that has been written to create immediate logical graphs from various types of R objects.
+`hchart()` will detect the R object type and decide the best way to plot it.
+Here are some examples.
+Notice that the function call is exactly the same `hchart([object])` but the plot that's produced is very different.
+
+Various other object types are supported which you can find [here](http://jkunst.com/highcharter/hchart.html)
+
+### Numeric Vector :: Histogram
+
+```{r}
+starwars %>%
+  pull(mass) %>%
+  hchart(name = class(.))
+```
+
+### Density Object :: Density Plot
+
+```{r}
+starwars %>%
+  filter(!is.na(mass)) %>%
+  pull(mass) %>%
+  density() %>%
+  hchart(name = class(.))
+```
+
+### Forecast Object :: Timeseries / Forecast Chart
+
+```{r}
+storms %>%
+  filter(name == "Emily") %>%
+  pull(wind) %>%
+  forecast() %>%
+  hchart(name = class(.))
+```
+
+## hchart() + hcaes()
+
+The most practical use of `hchart()` however is to use it like you would the `ggplot()` function.
+The implementation is slightly different - you have to specify your geom type inside the `hchart()` call for example - but the
 
@@
 This is normally a great and useful feature of highcharts but it's something to keep track of as you plot.
-
-## hchart()
-
-The `hchart()` function is kind of an amazing function that has been written to create immediate logical graphs from various types of R objects.
-`hchart()` will detect the R object type and decide the best way to plot it.
-Here are some examples.
-Notice that the function call is exactly the same `hchart([object])` but the plot that's produced is very different.
-
-### Numeric Vector -> Histogram
-
-```{r}
-starwars %>%
-  pull(mass) %>%
-  hchart()
-```
-
-### R Density Object -> Density Plot
-
-```{r}
-starwars %>%
-  filter(!is.na(mass)) %>%
-  pull(mass) %>%
-  density() %>%
-  hchart()
-```
-
-### Forecast Object -> Timeseries / Forecast Chart
-
-## Links
-
-This is an R Markdown document. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.
-
-When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.
-You can embed an R code chunk like this:
-
-```{r cars}
-summary(cars)
-```
-
-## Including Plots
-
-You can also embed plots, for example:
-
-```{r pressure, echo=FALSE}
-plot(pressure)
-```
-
-Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.

### 2019-08-14 04_highcharter-handbook/highcharter-handbook.Rmd
HCHB work

@@
 
-## Overview
+## Intro
 
@@
 This guide will provide examples on how to create and customise various graphs whilst providing some tips on how to think about the package that will help you build and debug your charts.
+I'll try to show and explain (to the best of my knowledge) the most common graphs and customisation options I use in my day-to-day work.
 
-Your most important resource should be the highcharts api documentation which you should bookmark in your browser:
+Your most important resources should be the highcharter official website, and the highcharts api documentation which you should bookmark in your browser:
 
+* [Highcharter official website](http://jkunst.com/highcharter/)
 * [Highcharts API Documentation](https://api.highcharts.com/highcharts/)
 
-Using `highcharter` properly will involve learning a little javascript but not too much, and it's probably good for you.
+As you become more a more proficient `highcharter` user and your charting requirements become more complicated you will need to understand more about the complexities of the highcharts API and you might need to learn + read a little javascript.
+This learning curve is actually the best thing about highcharter: basic charts are as easy to create as `ggplot`, whilst complex / beautiful chars are still achievable with enough thought and tinkering.
 
-## Datasets
-
-I'll frequently be using the following two datasets:
+In the following examples I'll frequently be using the following two datasets:
 
@@
 * dplyr::storms | hurricane timeseries data
+
+## Basics
+
+### Tidy Data
+
+If your
+
+### Default charts
 

### 2019-08-16 04_highcharter-handbook/highcharter-handbook.Rmd
2nd work comp

@@
 library(forecast)
+library(ggplot2)
 knitr::opts_chunk$set(echo = TRUE)
@@
 Most of the highcharts functionality is implemented through `highcharter` however the documentation is somewhat limited.
-This guide will provide examples on how to create and customise various graphs whilst providing some tips on how to think about the package that will help you build and debug your charts.
+This guide will provide examples on how to create and customise various graphs whilst providing some tips on how to think about the package that will help you build and debug your more ambitious charts.
 I'll try to show and explain (to the best of my knowledge) the most common graphs and customisation options I use in my day-to-day work.
 
-Your most important resources should be the highcharter official website, and the highcharts api documentation which you should bookmark in your browser:
+Your most important resources should be the `highcharter` official website, and the highcharts api documentation which you should bookmark in your browser:
 
-* [Highcharter official website](http://jkunst.com/highcharter/)
+* [Highcharter Official Website](http://jkunst.com/highcharter/)
 * [Highcharts API Documentation](https://api.highcharts.com/highcharts/)
@@
 
-If your
+Most (~90%) of your day-to-day charts can be probably written with 2-3 lines of code using the `hchart` and `hcaes` functions. These functions allow you packages `ggplot` like syntax. That is if your
+
+In `highcharter`, `ggplot`'s grammar of graphics aesthetic mapping is supported through the `hchart()` function.
+
+A simple `ggplot` call might look like the following:
+
+```{r message=FALSE, warning=FALSE}
+ggplot(starwars, aes(x = name, y = height)) +
+  geom_col()
+```
+
+This chart (let's be honest here) looks awful.
+For full disclosure `ggplot` has a number of functional advantages over highcharter as it has simple implementations of reasonably complex chart types.
+But highcharter creates quick, readable, nice looking default charts that can be presented in a usable publishing format (a html page) a thousand times better than ggplot.
+
+Here's the highcharter version of this plot:
+
+```{r message=FALSE, warning=FALSE}
+hchart(starwars, "column", hcaes(x = name, y = height))
+```
+
+There's a number of things you might notice about this chart and how it differs from it's ggplot counterpart.
+
+* 
+* t thing is that if you can interact with it; hover over it to see a (relatively ugly) tooltip.
+Second is that it's dynamic, which you'll notice initially because there are more bars (star wars characters) than there are labels on the y-axis.
+To see an exaggerated version of this reduce the width of your browser window to see the chart react and replot as it tries to estimate the best way to present the data without it looking busy and cluttered; the number of characters shown on the y-axis will keep decreasing.
+
+This is normally a great and useful feature of highcharts but it's something to keep track of as you plot.
 
@@
 ```
-
-## hchart() + hcaes()
-
-The most practical use of `hchart()` however is to use it like you would the `ggplot()` function.
-The implementation is slightly different - you have to specify your geom type inside the `hchart()` call for example - but the
-
-```{r}
-hchart(starwars, "column", hcaes(x = name, y = height))
-```
-
-There's a number of things you might notice about this chart if you've spent a bit of time graphing in R.
-First thing is that if you can interact with it; hover over it to see a (relatively ugly) tooltip.
-Second is that it's dynamic, which you'll notice initially because there are more bars (star wars characters) than there are labels on the y-axis.
-To see an exaggerated version of this reduce the width of your browser window to see the chart react and replot as it tries to estimate the best way to present the data without it looking busy and cluttered; the number of characters shown on the y-axis will keep decreasing.
-
-This is normally a great and useful feature of highcharts but it's something to keep track of as you plot.
